---
title: "CCS Analysis Template"
author: "Corey Jackson"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float:
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Import example data
library(readr)
library(reshape2)
library(dplyr)
library(tidygeocoder)
library(tidycensus)
library(tidyverse)
library(googleLanguageR)
library(cld2)
library(datasets)
library(textstem)
library(tidytext)
library(DT)
library(ggraph)
library(igraph)
library(RColorBrewer)
library(ggthemes)
library(tm)
library(tidytext)
library(textdata)
library(topicmodels)
###########################################################
####### IMPORT/COMBINE DATASETS FROM RESEARCH DRIVE #######
###########################################################

# Import file survey and map files from Research Drive. Ignore the first 7 lines that have metadata for the element
heat_survey <- read_csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/urban-heat/heat_survey.csv") 
heat_survey <- heat_survey[,-1]

tree_survey <- read_csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/tree-canopy/tree_survey.csv") 
tree_survey <- tree_survey[,-1]

air_survey <- read_csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/air-quality/air_survey.csv") 
air_survey <- air_survey[,-1]

ej_survey <- read_csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/ej-survey/ej_survey.csv") 
ej_survey <- ej_survey[,-1]

oct_general <- read_csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/deliberation/oct_general.csv") 
```

# CCS Knowledge Map Response Analysis Template

There are four types of questions, we asked in the CCS surveys, the Knowledge Map will need to detect the question type and conduct analysis based on the type of question present

## Short/long Text Questions

These questions are open ended and include text responses. The set of questions will be cleaned using text mining procedures and then analyzed using bag of words and sentiment. The presentation of responses will be word clouds and sentiment by the demographic factors. Example question is Heat Survey Q1 "Have you or anyone you know experienced health issues related to urban heat (e.g., heat exhaustion, heat stroke) in the past year? If so, please tell us a bit about the persons' experiences."

### Cleaning Open-ended Response Data 

```{r cleaning-openended-response}

# https://www.tidytextmining.com/index.html 

# Import stoplist 
malletwords <- scan("/Volumes/cbjackson2/ccs-knowledge/ccs-data/report_data/mallet.txt", character(), quote = "")

# Extract example question and demographic data
example_open <- heat_survey[,c(2,4,45:53,19)]
names(example_open)[2] <- "response" 

example_open$response_cleaned <- tolower(gsub('[[:punct:]]', ' ', example_open$response))
example_open$response_cleaned <- removeWords(example_open$response_cleaned, c(stopwords("english"),malletwords))
example_open$response_cleaned <- lemmatize_words(example_open$response_cleaned)

# Tokenize response_cleaned to create word cloud and summary responses by demographic groups
unigram_response <- example_open %>% 
  unnest_tokens(unigram, 
                response_cleaned, token = "ngrams", n = 1)

# Melt data
unigram_response.m <- unigram_response %>%
  pivot_longer(!`Contribution ID`:Gender, names_to = "tokens", values_to = "word")

# Summarize data by demographic factors - Gender, Hipanic/Latino/Spanish Origin, Race / Ethnicity, Year of Birth, Annual Household Income level, Education Level
unigram_summary <- unigram_response.m %>% 
  group_by(income_recode,word) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove infrequent categories. IF category has smaller than +/- 2 SDs remove from response data 
# unigram_constraint <- unigram_summary %>% 
#   group_by(Gender) %>% 
#   summarise(count = n()) %>%
#   mutate(freq = round(count / sum(count),digits=2))
# 
# # REMOVE RESPONSES WITH LESS THAN 10 percent of total or NA
# unigram_summary <- unigram_summary %>%
#       filter(!is.na(Gender))  %>%
#       filter(!Gender %in% unigram_constraint$Gender[which(unigram_constraint$freq <= .10 | is.na(unigram_constraint$Gender))])
# 
# top_unigram_words <- unigram_summary %>%
#   group_by(Gender) %>%
#   arrange(-freq) %>%
#   slice_head(n=20) %>%
#   ungroup()
# 
# # GET COLORS FOR ALL DEMOGRAPHIC VARIABLES
# gender_options <- c(NA,"Non-binary","Male","Female") # Called multi-options in previous
# col_pal<-brewer.pal(length(gender_options),"PuOr")
# gender_color_mapping <- data.frame(Gender = gender_options, col = col_pal) # Formerly gender_color_mapping
# 
# top_unigram_words <- merge(top_unigram_words, gender_color_mapping, by = "Gender")
# 
# unigram_plot <- ggplot(top_unigram_words, aes(x = reorder(word, freq), y = freq, fill=col)) +
#   geom_bar(stat="identity", color="black", 
#            position=position_dodge(width = 0.7, preserve = "single")) +
#   scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
#   coord_flip() +
#   facet_wrap(~Gender, scales = "free_y") +
#   ggtitle(paste0("Word Frequency By ",names(unigram_summary)[1])) + 
#   labs(x = "Unigram",y = "Frequency") 
# 
#       
###### BIGRAMS
bigram_response <- example_open %>% 
  unnest_tokens(unigram, 
                response_cleaned, token = "ngrams", n = 2)

bigram_response.m <- bigram_response %>%
  pivot_longer(!`Contribution ID`:Gender, names_to = "tokens", values_to = "word")

# Summarize data by demographic factors - Gender, Hipanic/Latino/Spanish Origin, Race / Ethnicity, Year of Birth, Annual Household Income level, Education Level
bigram_summary <- bigram_response.m %>% 
  group_by(income_recode,word) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove infrequent categories. IF category has smaller than +/- 2 SDs remove from response data 
# bigram_constraint <- bigram_summary %>% 
#   group_by(Gender) %>% 
#   summarise(count = n()) %>%
#   mutate(freq = round(count / sum(count),digits=2))
# 
# # REMOVE RESPONSES WITH LESS THAN 10 percent of total or NA
# bigram_summary <- bigram_summary %>%
#       filter(!is.na(Gender))  %>%
#       filter(!Gender %in% bigram_constraint$Gender[which(bigram_constraint$freq <= .10 | is.na(bigram_constraint$Gender))])
# 
# top_bigram_words <- bigram_summary %>%
#   group_by(Gender) %>%
#   arrange(-freq) %>%
#   slice_head(n=20) %>%
#   ungroup()
# 
# top_bigram_words <- merge(top_bigram_words, gender_color_mapping, by = "Gender")
# 
# bigram_plot <- ggplot(top_bigram_words, aes(x = reorder(word, freq), y = freq, fill=col)) +
#   geom_bar(stat="identity", color="black", 
#            position=position_dodge(width = 0.7, preserve = "single")) +
#   scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
#   coord_flip() +
#   facet_wrap(~Gender, scales = "free_y") +
#   ggtitle(paste0("Word Frequency By ",names(unigram_summary)[1])) + 
#   labs(x = "Bi-gram",y = "Frequency") 

###################################
# POTENTIAL ANALYSES OF RESPONSES #
###################################
```

```{r cleaning-openended-response-graph}
## 1. GRAPH
   #### https://chryswoods.com/text_analysis_r/ngrams.html 
   #### https://www.data-imaginist.com/2017/ggraph-introduction-layouts/
   #### https://cran.r-project.org/web/packages/ggraph/vignettes/Layouts.html 
   #### CAN BE USED TO SHOW OVERLAPPING AND UNIQUE RESPONSES BY GROUP. HOW TO CREATE NARRATIVE AND HELP USERS READ AND INTERPRET CHART


# OTHER TUTORIALS 
### https://rpubs.com/neloe/ggraph_intro 
### https://ggraph.data-imaginist.com/ 
### http://users.dimi.uniud.it/~massimo.franceschet/ns/syllabus/make/ggraph/ggraph.html 

### UNIGRAM
unigram_summary <- unigram_summary[which(!is.na(unigram_summary$word)),]

unigram_graph <- unigram_summary %>%
  filter(freq >= .02) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = freq, edge_width = freq), edge_colour = "darkred") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) + 
  theme_void() 
   
### BIGRAM
bigram_graph <- bigram_summary %>%
  filter(freq >= .02) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = count, edge_width = count), edge_colour = "darkred") +
  geom_node_point(size = 5) +
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()

```


```{r cleaning-openended-response-sentiment, eval=FALSE, render=FALSE}

# 2. SENTIMENT ANALYSIS

  #### https://www.tidytextmining.com/sentiment
  #### THERE ARE THREE DICTIONARIES FOR SENTIMENT AFFIN, NRC, AND BING. (NRC REPRESENTS MANY MORE EMPOTIONAL CATEGORIES)

nrc_S <- get_sentiments("nrc") %>% 
  filter(!sentiment %in% c("positive", "negative"))

# UNIGRAM
unigram_summary <- unigram_summary %>%
  inner_join(nrc_S)

# PLOT SENTIMENT WITH PROPORTION OF WORDS
unigram_sentiment_summary <- unigram_summary %>% 
  group_by(Gender,sentiment) %>% 
  summarise(total_words = sum(count)) %>%
  mutate(freq = round(total_words / sum(total_words),digits=2))

color_sentiment <- data.frame (sentiment  = c("anger","anticipation","disgust",
                                           "fear","joy","sadness","surprise", "trust"),
                  col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99",
                          "#E6A1A1","#8A75E6","#B89EE6") #https://color.adobe.com/create/color-wheel
                  )
unigram_sentiment_summary <- merge(unigram_sentiment_summary,color_sentiment, by="sentiment")

# SENTIMENT FACETED BY GENDER
unigram_sentiment_plot <- ggplot(unigram_sentiment_summary, aes(x = reorder(sentiment, freq), y = freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single")) +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  coord_flip() +
  facet_wrap(~Gender, scales = "free_y") +
  ggtitle(paste0("Sentiment By ",names(unigram_summary)[1])) + 
  labs(x = "Emotion",y = "Frequency") 

# WORDS FACETED BY SENTIMENT 
unigram_summary <- merge(unigram_summary, gender_color_mapping, by = "Gender")

unigram_sentiment_plot2 <- unigram_summary %>%
  group_by(Gender,sentiment) %>%
  slice_max(count, n = 5) %>% 
  ungroup() %>%
  mutate(word = reorder(word, count)) %>%
  ggplot(aes(count, word, fill = col)) +
  geom_col(show.legend = FALSE,position=position_dodge(width = 0.7, preserve = "single")) +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL) + 
  theme(
     axis.text = element_text(size = 8))
```

```{r cleaning-openended-response-topic, eval=FALSE, render=FALSE}
# 3. TOPIC MODELING

# EACH COMMENT IS A DOCUMENT. EXTRACT WORD AND CONTRIBUTION ID
doc_summary <- unigram_response.m %>% 
  group_by(`Contribution ID`,Gender, word) %>% 
  #group_by(Gender,word) %>% 
  summarise(count = n()) %>%
  filter_at(vars(Gender, word), all_vars(!is.na(.)))

# FOR EACH DEMOGRAPHIC VARIABLE RUN TOPIC MODELS
topic_models =  data.frame()

for (i in unique(doc_summary$Gender)) {
  
  doc_summary_loop <- doc_summary[which(doc_summary$Gender == i),]
  
  doc.dtm <- doc_summary_loop %>%
  cast_dtm(`Contribution ID`, word, count)
  
  tm_lda <- LDA(doc.dtm, k = 3)
  tm_topics <- tidy(tm_lda, matrix = "beta")

  tm_top_terms <- tm_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 5) %>% 
  ungroup() %>%
  arrange(topic, -beta)
  tm_top_terms$Gender  <- i 
  ## APPEND ALL TO SINGLE DATAFRAME
  topic_models <- rbind(topic_models,tm_top_terms)
}

topic_models <- merge(topic_models,gender_color_mapping, by ="Gender")


  # ggplot(topic_models, aes(beta, term, fill = factor(topic))) +
  # geom_col(show.legend = FALSE) +
  # facet_wrap(~ topic, scales = "free") +
  # scale_y_reordered()


# doc.dtm <- doc_summary %>%
# cast_dtm(`Contribution ID`, word, count)
# 
# tm_lda <- LDA(doc.dtm, k = 3)
# tm_topics <- tidy(tm_lda, matrix = "beta")
# 
# tm_top_terms <- tm_topics %>%
#   group_by(topic) %>%
#   slice_max(beta, n = 5) %>% 
#   ungroup() %>%
#   arrange(topic, -beta)
# 
# topic_viz <- tm_top_terms %>%
#   mutate(term = reorder_within(term, beta, topic)) %>%
#   ggplot(aes(beta, term, fill = factor(topic))) +
#   geom_col(show.legend = FALSE) +
#   facet_wrap(~ topic, scales = "free") +
#   scale_y_reordered()

```

### Reporting Open Ended Responses

#### Graph Based 
```{r reporting-openended-response-graph}
datatable(unigram_summary)

unigram_graph

datatable(bigram_summary)

bigram_graph
```

```{r reporting-openended-response-sentiment, render=FALSE, eval=FALSE}
#### Option 2: Sentiment Analysis

datatable(unigram_sentiment_summary[, c(1:4), drop=FALSE]) %>%
  formatStyle('Gender',
  backgroundColor = styleEqual(gender_color_mapping$Gender, gender_color_mapping$col)
  )

unigram_sentiment_plot

unigram_sentiment_plot2
```

```{r reporting-openended-response-topic, render=FALSE, eval=FALSE}
#### Option 3: Topic Modeling
plot_Female

plot_Male

plot_Non-binary
```


## Matrix Questions

Example question is Heat Survey Q2 "Please rate how frequently you have done each of the following during summer months and during extreme heat."

### Cleaning Matrix Responses  

Detection might involve extracting the first four words of every response, if they all match, then the response is a multi-choice data object. 

```{r cleaning-matrix-response}

###### PREPROCESSING FOR CCS QUESTIONS  ######
example_matrix <- heat_survey[,c(2,5,45:53,19)] # ORIGINAL EXAMPLE
names(example_matrix)[2] <- "response" 


example_matrix <- ej_survey[,c(2,7,50:58,24)] # CHECKING
names(example_matrix)[2] <- "response" 

# Since the questions are in one column, we need to seperate them and then the question and respone variables. ONLY FOR CCS QUESTIONS. In the allquestions_types questions in the CCS column = 1
example_matrix <- example_matrix %>% 
  separate_rows(response, sep = "; ") %>%
  separate(response, into = c("question", "answer"), sep = " - ")
example_matrix$answer <- as.factor(example_matrix$answer)

matrix_summary <- example_matrix %>% 
  group_by(Gender,question,answer) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) 

matrix_summary <- matrix_summary %>%
      filter(!is.na(Gender)) # SHOULD BE FOR ALL DATAFRAMES IF THE VARIABLE IS NA

###### PREPROCESSING FOR OPEN DELIBERATION QUESTIONS  ######
example_matrix_deliberation <- oct_general[,c(1,15,24:28)]
example_matrix_deliberation$question <- names(example_matrix_deliberation)[2]
names(example_matrix_deliberation)[2] <- c("answer")  

matrix_summary_deliberation <- example_matrix_deliberation %>% 
  group_by(gender,question,answer) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) 

############## FREQUENCY ##############
color_set_frequency <- data.frame (answer  = c("Always","Often","Sometimes","Rarely","Never"),
                   col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99")) 

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_frequency$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_frequency, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Always","Often")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Never", "Rarely")),]
mylevels <- c("Always","Often","Sometimes","Rarely","Never")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
  

############## AGREE 2 ##############
color_set_agree2 <- data.frame (answer  = c("Strongly agree","Agree","Neither Agree nor disagree","Disagree","Strongly disagree"), col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99")) 

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_agree2$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_agree2, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Strongly agree","Agree")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Disagree","Strongly disagree ")),]
mylevels <- c("Strongly agree","Agree","Neither Agree nor disagree","Disagree","Strongly disagree")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
  
  
############## AGREE 1 ##############
color_set_agree1 <- data.frame (answer  = c("Strongly agree","Agree","Neutral","Disagree","Strongly disagree"), col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99")) 

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_agree1$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_agree1, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Strongly agree","Agree")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Disagree","Strongly disagree ")),]
mylevels <- c("Strongly agree","Agree","Neutral","Disagree","Strongly disagree")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
  
############## AGREE ##############
color_set_agree <- data.frame (answer  = c("Agree Strongly","Agree Somewhat","Neutral","Disagree Somewhat","Disagree Strongly"), col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99")) 

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_agree$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_agree, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Agree Strongly","Agree Somewhat")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Disagree Somewhat","Disagree Strongly")),]
mylevels <- c("Agree Strongly","Agree Somewhat","Neutral","Disagree Somewhat","Disagree Strongly")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
  

############## AWARENESS ##############
color_set_awareness <- data.frame (answer  = c("Aware","Not Aware"),
                   col = c("#E66101","#5E3C99"))

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_awareness$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_awareness, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Aware")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Not Aware")),]
mylevels <- c("Aware","Not Aware")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
  
############## INFORMED ##############
color_set_informed <- data.frame (answer  = c("Very Informed","Informed","Moderately Informed","Slightly Informed","Not at all Informed"),
                   col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99"))
  
# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_informed$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_informed, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Very Informed","Informed")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Slightly Informed","Not at all Informed")),]
mylevels <- c("Very Informed","Informed","Moderately Informed","Slightly Informed","Not at all Informed")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
 
############## AMOUNT ##############
color_set_amount <- data.frame (answer  = c("A lot","A Good Amount","Some","A Little","Nothing"),
                   col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99"))

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_amount$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_amount, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("A lot","A Good Amount")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("A Little","Nothing")),]
mylevels <- c("A lot","A Good Amount","Some","A Little","Nothing")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
 
############## BINARY ##############
color_set_binary <- data.frame (answer  = c("Yes","No"),
                   col = c("#E66101","#5E3C99"))

  # Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_binary$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_binary, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Yes")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("No")),]
mylevels <- c("Yes","No")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
 
############## IMPORTANCE ##############
color_set_importance <- data.frame (answer  = c("Extremely Unimportant","Very Unimportant","Somewhat Unimportant","Neither Important nor Unimportant","Somewhat Important","Very Important","Extremely Important"),col = 
                                            c("#E66101","#FDB863","#FAE9D6","#F7F7F7","#B2ABD2","#6753D7","#3F009E")) 

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_importance$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal


matrix_summary <- merge(matrix_summary,color_set_importance, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Extremely Unimportant","Very Unimportant","Somewhat Unimportant")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Somewhat Important","Very Important","Extremely Important")),]
mylevels <- c("Extremely Unimportant","Very Unimportant","Somewhat Unimportant","Neither Important nor Unimportant","Somewhat Important","Very Important","Extremely Important")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
  
############## CHANGE ##############
color_set_fchange <- data.frame (answer  = c("Increased","Decreased","Stayed the same","I don't Know"),col = c("#E66101","#FDB863","#3F009E","#F7F7F7")) 

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(color_set_fchange$answer)
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- merge(matrix_summary,color_set_fchange, by="answer")
# merge colors with dataframe

# TRANSFORM HIGH/LOWS
highs <- matrix_summary[which(matrix_summary$answer %in% c("Increased")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Decreased")),]
mylevels <- c("Increased","Decreased","Stayed the same","I don't Know")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25))

```


### Reporting Matrix Responses  
```{r}
datatable(matrix_summary)

matrix_visualization
```


## Multi-Choice Questions

### Cleaning Multi-Choice Responses 
```{r}
example_multi <- heat_survey[,c(2,7,45:53,19)]  
names(example_multi)[2] <- "response" 

example_multi <- example_multi %>% 
  separate_rows(response, sep = "; ")

# Also extract other and run topic modeling? 
multi_summary <- example_multi %>% 
  group_by(Gender,response) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove other responses
multi_summary <- multi_summary %>%
    filter(!grepl("^Other \\(please specify\\)", response)) %>%
    filter(!is.na(Gender))  %>%
    filter(!Gender == "Non-binary")

multi_summary <- merge(multi_summary, gender_color_mapping, by = "Gender")

# Visualization (HORIZONTAL BAR CHART)
multi_visualization <-
  ggplot(data=multi_summary, aes(x=response, y=freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single"))+
  labs(y="Percent of Respondents") +
  coord_flip() + 
  theme_classic() +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  theme(
    legend.position="bottom",axis.title.y = element_blank(),
     axis.text = element_text(size = 8))
```

### Reporting Multi-Choice Responses 
```{r}
datatable(multi_summary[, c(1:4), drop=FALSE]) %>%
  formatStyle('Gender',
  backgroundColor = styleEqual(gender_color_mapping$Gender, gender_color_mapping$col)
  )

multi_visualization
```


## Select Box Questions

Trees question #4 has select box question

### Cleaning Select Box Responses 
```{r}
example_select <- tree_survey[,c(2,7,22,48:56)]
names(example_select)[2] <- "response" 

select_summary <- example_select %>% 
  group_by(Gender,response) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove other responses
select_summary <- select_summary %>%
    filter(!grepl("^Other \\(please specify\\)", response)) %>%
    filter(!is.na(Gender))  %>%
    filter(!Gender == "Non-binary")

select_summary <- merge(select_summary, gender_color_mapping, by = "Gender") # USE SAME COLORS FROM OTHER

select_visualization <-
  ggplot(data=select_summary, aes(x=response, y=freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single"))+
  labs(y="Count") +
  coord_flip() + 
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  #facet_grid(. ~Gender)  +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  theme(
    legend.position="bottom",axis.title.y = element_blank(),
     axis.text = element_text(size = 8))

```

### Reporting Select Box Responses 
```{r}
datatable(select_summary[, c(1:4), drop=FALSE]) %>%
  formatStyle('Gender',
  backgroundColor = styleEqual(gender_color_mapping$Gender, gender_color_mapping$col)
  )

select_visualization
```

