---
title: "CCS Analysis Template"
author: "Corey Jackson"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float:
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Import example data
library(readr)
library(reshape2)
library(dplyr)
library(tidygeocoder)
library(tidycensus)
library(tidyverse)
library(googleLanguageR)
library(cld2)
library(datasets)
library(textstem)
library(tidytext)
library(DT)
library(ggraph)
library(igraph)
library(RColorBrewer)
library(ggthemes)
library(tm)
library(tidytext)
library(textdata)
library(topicmodels)
###########################################################
####### IMPORT/COMBINE DATASETS FROM RESEARCH DRIVE #######
###########################################################

# Import file survey and map files from Research Drive. Ignore the first 7 lines that have metadata for the element
heat_survey <- read_csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/urban-heat/heat_survey.csv") 
heat_survey <- heat_survey[,-1]

tree_survey <- read_csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/tree-canopy/tree_survey.csv") 
tree_survey <- tree_survey[,-1]


#### GENDER SETUP
gender_options <- c(NA,"Non-binary","Male","Female") # Called multi-options in previous
col_pal<-brewer.pal(length(gender_options),"PuOr")
gender_color_mapping <- data.frame(Gender = gender_options, col = col_pal) # Formerly gender_color_mapping


## MAPPING NEEDED FOR OTHER OUTPUTS OF CATEGORIES

#### AGE

#### CHOICES


```

# CCS Knowledge Map Response Analysis Template

There are four types of questions, we asked in the CCS surveys, the Knowledge Map will need to detect the question type and conduct analysis based on the type of question present

## Short/long Text Questions

These questions are open ended and include text responses. The set of questions will be cleaned using text mining procedures and then analyzed using bag of words and sentiment. The presentation of responses will be word clouds and sentiment by the demographic factors. Example question is Heat Survey Q1 "Have you or anyone you know experienced health issues related to urban heat (e.g., heat exhaustion, heat stroke) in the past year? If so, please tell us a bit about the persons' experiences."

### Cleaning Open-ended Response Data 

```{r cleaning-openended-response}

# https://www.tidytextmining.com/index.html 
# https://paldhous.github.io/NICAR/2019/r-text-analysis.html 

# Import stoplist 
malletwords <- scan("/Volumes/cbjackson2/ccs-knowledge/ccs-data/report_data/mallet.txt", character(), quote = "")

# Extract example question and demographic data
example_open <- heat_survey[,c(2,4,45:53,19)]
names(example_open)[2] <- "response" 

example_open$response_cleaned <- tolower(gsub('[[:punct:]]', ' ', example_open$response))
example_open$response_cleaned <- removeWords(example_open$response_cleaned, c(stopwords("english"),malletwords))
example_open$response_cleaned <- lemmatize_words(example_open$response_cleaned)

# Tokenize response_cleaned to create word cloud and summary responses by demographic groups
unigram_response <- example_open %>% 
  unnest_tokens(unigram, 
                response_cleaned, token = "ngrams", n = 1)

# Melt data
unigram_response.m <- unigram_response %>%
  pivot_longer(!`Contribution ID`:Gender, names_to = "tokens", values_to = "word")

# Summarize data by demographic factors - Gender, Hipanic/Latino/Spanish Origin, Race / Ethnicity, Year of Birth, Annual Household Income level, Education Level
unigram_summary <- unigram_response.m %>% 
  group_by(Gender,word) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove infrequent categories. IF category has smaller than +/- 2 SDs remove from response data 
unigram_constraint <- unigram_summary %>% 
  group_by(Gender) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# REMOVE RESPONSES WITH LESS THAN 10 percent of total or NA
unigram_summary <- unigram_summary %>%
      filter(!is.na(Gender))  %>%
      filter(!Gender %in% unigram_constraint$Gender[which(unigram_constraint$freq <= .10 | is.na(unigram_constraint$Gender))])

top_unigram_words <- unigram_summary %>%
  group_by(Gender) %>%
  arrange(-freq) %>%
  slice_head(n=20) %>%
  ungroup()

top_unigram_words <- merge(top_unigram_words, gender_color_mapping, by = "Gender")

unigram_plot <- ggplot(top_unigram_words, aes(x = reorder(word, freq), y = freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single")) +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  coord_flip() +
  facet_wrap(~Gender, scales = "free_y") +
  ggtitle(paste0("Word Frequency By ",names(unigram_summary)[1])) + 
  labs(x = "Unigram",y = "Frequency") 

      
###### BIGRAMS
bigram_response <- example_open %>% 
  unnest_tokens(unigram, 
                response_cleaned, token = "ngrams", n = 2)

bigram_response.m <- bigram_response %>%
  pivot_longer(!`Contribution ID`:Gender, names_to = "tokens", values_to = "word")

# Summarize data by demographic factors - Gender, Hipanic/Latino/Spanish Origin, Race / Ethnicity, Year of Birth, Annual Household Income level, Education Level
bigram_summary <- bigram_response.m %>% 
  group_by(Gender,word) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove infrequent categories. IF category has smaller than +/- 2 SDs remove from response data 
bigram_constraint <- bigram_summary %>% 
  group_by(Gender) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# REMOVE RESPONSES WITH LESS THAN 10 percent of total or NA
bigram_summary <- bigram_summary %>%
      filter(!is.na(Gender))  %>%
      filter(!Gender %in% bigram_constraint$Gender[which(bigram_constraint$freq <= .10 | is.na(bigram_constraint$Gender))])

top_bigram_words <- bigram_summary %>%
  group_by(Gender) %>%
  arrange(-freq) %>%
  slice_head(n=20) %>%
  ungroup()

top_bigram_words <- merge(top_bigram_words, gender_color_mapping, by = "Gender")

bigram_plot <- ggplot(top_bigram_words, aes(x = reorder(word, freq), y = freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single")) +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  coord_flip() +
  facet_wrap(~Gender, scales = "free_y") +
  ggtitle(paste0("Word Frequency By ",names(unigram_summary)[1])) + 
  labs(x = "Bi-gram",y = "Frequency") 

###################################
# POTENTIAL ANALYSES OF RESPONSES #
###################################
```

```{r cleaning-openended-response-graph}
## 1. GRAPH
   #### https://chryswoods.com/text_analysis_r/ngrams.html 
   #### https://www.data-imaginist.com/2017/ggraph-introduction-layouts/
   #### https://cran.r-project.org/web/packages/ggraph/vignettes/Layouts.html 
   #### CAN BE USED TO SHOW OVERLAPPING AND UNIQUE RESPONSES BY GROUP. HOW TO CREATE NARRATIVE AND HELP USERS READ AND INTERPRET CHART


# OTHER TUTORIALS 
### https://rpubs.com/neloe/ggraph_intro 
### https://ggraph.data-imaginist.com/ 
### http://users.dimi.uniud.it/~massimo.franceschet/ns/syllabus/make/ggraph/ggraph.html 

### UNIGRAM
unigram_graph <- unigram_summary %>%
                  group_by(Gender) %>%
                  arrange(-freq) %>%
                  slice_head(n=50) %>%
                  select(word) %>%
                  graph_from_data_frame()

ggraph(unigram_graph, layout = 'fr') +
  geom_edge_link() +
  geom_node_point(aes(size = size)) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)


# What we should highlight - items common among the populations and text that are unique within the population. 

### BIGRAM
bigram_graph <- bigram_summary %>%
                  group_by(Gender) %>%
                  arrange(-freq) %>%
                  slice_head(n=50) %>%
                  select(word) %>%
                  graph_from_data_frame()

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)

```


```{r cleaning-openended-response-sentiment, eval=FALSE, render=FALSE}

# 2. SENTIMENT ANALYSIS

  #### https://www.tidytextmining.com/sentiment
  #### THERE ARE THREE DICTIONARIES FOR SENTIMENT AFFIN, NRC, AND BING. (NRC REPRESENTS MANY MORE EMPOTIONAL CATEGORIES)

nrc_S <- get_sentiments("nrc") %>% 
  filter(!sentiment %in% c("positive", "negative"))

# UNIGRAM
unigram_summary <- unigram_summary %>%
  inner_join(nrc_S)

# PLOT SENTIMENT WITH PROPORTION OF WORDS
unigram_sentiment_summary <- unigram_summary %>% 
  group_by(Gender,sentiment) %>% 
  summarise(total_words = sum(count)) %>%
  mutate(freq = round(total_words / sum(total_words),digits=2))

color_sentiment <- data.frame (sentiment  = c("anger","anticipation","disgust",
                                           "fear","joy","sadness","surprise", "trust"),
                  col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99",
                          "#E6A1A1","#8A75E6","#B89EE6") #https://color.adobe.com/create/color-wheel
                  )
unigram_sentiment_summary <- merge(unigram_sentiment_summary,color_sentiment, by="sentiment")

# SENTIMENT FACETED BY GENDER
unigram_sentiment_plot <- ggplot(unigram_sentiment_summary, aes(x = reorder(sentiment, freq), y = freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single")) +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  coord_flip() +
  facet_wrap(~Gender, scales = "free_y") +
  ggtitle(paste0("Sentiment By ",names(unigram_summary)[1])) + 
  labs(x = "Emotion",y = "Frequency") 

# WORDS FACETED BY SENTIMENT 
unigram_summary <- merge(unigram_summary, gender_color_mapping, by = "Gender")

unigram_sentiment_plot2 <- unigram_summary %>%
  group_by(Gender,sentiment) %>%
  slice_max(count, n = 5) %>% 
  ungroup() %>%
  mutate(word = reorder(word, count)) %>%
  ggplot(aes(count, word, fill = col)) +
  geom_col(show.legend = FALSE,position=position_dodge(width = 0.7, preserve = "single")) +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL) + 
  theme(
     axis.text = element_text(size = 8))
```

```{r cleaning-openended-response-topic, eval=FALSE, render=FALSE}
# 3. TOPIC MODELING

# EACH COMMENT IS A DOCUMENT. EXTRACT WORD AND CONTRIBUTION ID
doc_summary <- unigram_response.m %>% 
  group_by(`Contribution ID`,Gender, word) %>% 
  #group_by(Gender,word) %>% 
  summarise(count = n()) %>%
  filter_at(vars(Gender, word), all_vars(!is.na(.)))

# FOR EACH DEMOGRAPHIC VARIABLE RUN TOPIC MODELS
topic_models =  data.frame()

for (i in unique(doc_summary$Gender)) {
  
  doc_summary_loop <- doc_summary[which(doc_summary$Gender == i),]
  
  doc.dtm <- doc_summary_loop %>%
  cast_dtm(`Contribution ID`, word, count)
  
  tm_lda <- LDA(doc.dtm, k = 3)
  tm_topics <- tidy(tm_lda, matrix = "beta")

  tm_top_terms <- tm_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 5) %>% 
  ungroup() %>%
  arrange(topic, -beta)
  tm_top_terms$Gender  <- i 
  ## APPEND ALL TO SINGLE DATAFRAME
  topic_models <- rbind(topic_models,tm_top_terms)
}

topic_models <- merge(topic_models,gender_color_mapping, by ="Gender")


  # ggplot(topic_models, aes(beta, term, fill = factor(topic))) +
  # geom_col(show.legend = FALSE) +
  # facet_wrap(~ topic, scales = "free") +
  # scale_y_reordered()


# doc.dtm <- doc_summary %>%
# cast_dtm(`Contribution ID`, word, count)
# 
# tm_lda <- LDA(doc.dtm, k = 3)
# tm_topics <- tidy(tm_lda, matrix = "beta")
# 
# tm_top_terms <- tm_topics %>%
#   group_by(topic) %>%
#   slice_max(beta, n = 5) %>% 
#   ungroup() %>%
#   arrange(topic, -beta)
# 
# topic_viz <- tm_top_terms %>%
#   mutate(term = reorder_within(term, beta, topic)) %>%
#   ggplot(aes(beta, term, fill = factor(topic))) +
#   geom_col(show.legend = FALSE) +
#   facet_wrap(~ topic, scales = "free") +
#   scale_y_reordered()

```

### Reporting Open Ended Responses

#### Graph Based 
```{r reporting-openended-response-graph}
datatable(unigram_summary)

unigram_graph

datatable(bigram_summary)

bigram_graph
```

```{r reporting-openended-response-sentiment, render=FALSE, eval=FALSE}
#### Option 2: Sentiment Analysis

datatable(unigram_sentiment_summary[, c(1:4), drop=FALSE]) %>%
  formatStyle('Gender',
  backgroundColor = styleEqual(gender_color_mapping$Gender, gender_color_mapping$col)
  )

unigram_sentiment_plot

unigram_sentiment_plot2
```

```{r reporting-openended-response-topic, render=FALSE, eval=FALSE}
#### Option 3: Topic Modeling
plot_Female

plot_Male

`plot_Non-binary`
```


## Matrix Questions

Example question is Heat Survey Q2 "Please rate how frequently you have done each of the following during summer months and during extreme heat."

### Cleaning Matrix Responses  

Detection might involve extracting the first four words of every response, if they all match, then the response is a multi-choice data object. 

```{r cleaning-matrix-response}
example_matrix <- heat_survey[,c(2,5,45:53,19)]
names(example_matrix)[2] <- "response" 
# Since the questions are in one column, we need to seperate them and then the question and respone variables
example_matrix <- example_matrix %>% 
  separate_rows(response, sep = "; ") %>%
  separate(response, into = c("question", "answer"), sep = " - ")
example_matrix$answer <- as.factor(example_matrix$answer)

matrix_summary <- example_matrix %>% 
  group_by(Gender,question,answer) %>% 
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) 

# Recode likert to three responses 
example_matrix <- example_matrix %>%
  mutate(
    likert_category = case_when(
      answer %in% c("Never", "Rarely") ~ "Infrequent",
      answer == "Sometimes" ~ "Moderate",
      answer %in% c("Often", "Always") ~ "Frequent",
      TRUE ~ NA_character_  # If there's any unexpected value, set it as NA
    )
  )

# Create high and lows tables with question, group, outcome (question), variable, value, and color
numlevels<-length(unique(example_matrix$answer))
pal<-brewer.pal((numlevels),"PuOr")
legend.pal<-pal

matrix_summary <- matrix_summary %>%
      filter(!is.na(Gender))  %>%
      filter(!Gender == "Non-binary")

color_set_frequency <- data.frame (answer  = c("Always","Often","Sometimes","Rarely","Never"),
                  col = c("#E66101","#FDB863","#F7F7F7","#B2ABD2","#5E3C99")) # https://color.adobe.com/create/color-wheel 
matrix_summary <- merge(matrix_summary,color_set_frequency, by="answer")
# merge colors

highs <- matrix_summary[which(matrix_summary$answer %in% c("Always","Often")),]
lows <- matrix_summary[which(matrix_summary$answer %in% c("Never", "Rarely")),]
mylevels <- c("Always","Often","Sometimes","Rarely","Never")

matrix_visualization <- ggplot() + 
  geom_bar(data=highs, aes(x = question, y=freq, fill=col), position="stack", stat="identity") +
  geom_bar(data=lows, aes(x = question, y=-freq, fill=col), position="stack", stat="identity") +
  facet_grid(. ~Gender)  +
  geom_hline(yintercept = 0, color =c("white")) +
  scale_fill_identity("Percent of Respondents", 
                      labels = mylevels, 
                      breaks=legend.pal, 
                      guide="legend") + 
  theme_classic() +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  labs(y="",x="") +
  theme(
        legend.position = "bottom"
        ) 
  scale_y_continuous(breaks=seq(-10,100,25), limits=c(20,100))
```


### Reporting Matrix Responses  
```{r}
datatable(matrix_summary)

matrix_visualization
```


## Multi-Choice Questions

### Cleaning Multi-Choice Responses 
```{r}
example_multi <- heat_survey[,c(2,7,45:53,19)]
names(example_multi)[2] <- "response" 

example_multi <- example_multi %>% 
  separate_rows(response, sep = "; ")

# Also extract other and run topic modeling? 
multi_summary <- example_multi %>% 
  group_by(Gender,response) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove other responses
multi_summary <- multi_summary %>%
    filter(!grepl("^Other \\(please specify\\)", response)) %>%
    filter(!is.na(Gender))  %>%
    filter(!Gender == "Non-binary")

multi_summary <- merge(multi_summary, gender_color_mapping, by = "Gender")

# Visualization (HORIZONTAL BAR CHART)
multi_visualization <-
  ggplot(data=multi_summary, aes(x=response, y=freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single"))+
  labs(y="Percent of Respondents") +
  coord_flip() + 
  theme_classic() +
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  theme(
    legend.position="bottom",axis.title.y = element_blank(),
     axis.text = element_text(size = 8))
```

### Reporting Multi-Choice Responses 
```{r}
datatable(multi_summary[, c(1:4), drop=FALSE]) %>%
  formatStyle('Gender',
  backgroundColor = styleEqual(gender_color_mapping$Gender, gender_color_mapping$col)
  )

multi_visualization
```


## Select Box Questions

Trees question #4 has select box question

### Cleaning Select Box Responses 
```{r}
example_select <- tree_survey[,c(2,7,22,48:56)]
names(example_select)[2] <- "response" 

select_summary <- example_select %>% 
  group_by(Gender,response) %>% 
  summarise(count = n()) %>%
  mutate(freq = round(count / sum(count),digits=2))

# Remove other responses
select_summary <- select_summary %>%
    filter(!grepl("^Other \\(please specify\\)", response)) %>%
    filter(!is.na(Gender))  %>%
    filter(!Gender == "Non-binary")

select_summary <- merge(select_summary, gender_color_mapping, by = "Gender") # USE SAME COLORS FROM OTHER

select_visualization <-
  ggplot(data=select_summary, aes(x=response, y=freq, fill=col)) +
  geom_bar(stat="identity", color="black", 
           position=position_dodge(width = 0.7, preserve = "single"))+
  labs(y="Count") +
  coord_flip() + 
  scale_fill_identity("Counts", labels = gender_options, breaks=gender_color_mapping, guide="legend") + 
  #facet_grid(. ~Gender)  +
  scale_x_discrete(labels = function(x) str_wrap(str_replace_all(x, "foo" , " "),width = 40)) + 
  theme(
    legend.position="bottom",axis.title.y = element_blank(),
     axis.text = element_text(size = 8))

```

### Reporting Select Box Responses 
```{r}
datatable(select_summary[, c(1:4), drop=FALSE]) %>%
  formatStyle('Gender',
  backgroundColor = styleEqual(gender_color_mapping$Gender, gender_color_mapping$col)
  )

select_visualization
```

