---
title: 'CCS Knowledge Map Results: Air Quality'
author: "Corey Jackson"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(DT)
library(ggsci)
library(gridExtra)
library(stringr)

potential_fakes <- c(316, 317, 318, 319, 320, 321, 322, 323, 324, 325, 327, 329,
                     330, 331, 332, 333, 334, 335, 336, 337, 338, 339, 340, 342, 343, 344, 345, 
                     346, 348, 349, 350, 351, 352, 353, 354, 355, 356, 358, 359, 360, 361, 
                     362, 363, 364, 365, 366, 367, 369, 370, 371, 372, 373, 374, 376, 378, 379, 380,
                     381, 382, 383, 384, 385, 389, 390, 391, 392, 392, 393, 395, 396, 397, 398, 399,18,23,28)

participant_geographies <- fread("/Volumes/cbjackson2/ccs-knowledge/ccs-data[papers]/participant_geographies.csv")


air_survey <- read.csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/air-quality/air_survey.csv")
air_survey <- air_survey %>%
  select(17,5:14) %>%
  filter(!`Member.ID` %in% potential_fakes)
## REPLACE GEOGRAPHY DATA

air_map <- read.csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/air-quality/air_map.csv")

# remove dupes
air_survey <- air_survey %>%
  distinct(Contribution.ID, .keep_all = TRUE)

# Questions - https://docs.google.com/document/d/1hl5Eb66a8j7TDE1EzzOF4eUjUguet5dMsw7UJydr_uY/edit


### ### ### ### ### ### ### ### ### ## 
### Functions for MATRIX QUESTIONS ### 
### ### ### ### ### ### ### ### ### ##

clean_matrix <- function(dataframe, column_name) {
  cleaned_data <- dataframe %>%
    separate_rows({{ column_name }}, sep = "; ") %>%
    separate({{ column_name }}, into = c("question", "answer"), sep = " - ")
  cleaned_data$answer <- as.factor(cleaned_data$answer)
  
  summary_data <- cleaned_data %>%
    group_by(question, answer) %>%
    summarise(n = n()) %>%
    mutate(freq = round((n / sum(n)),digits=2     )*100)
  
  return(summary_data)
}

viz_matrix <- function(dataframe, graph_title) {
  ggplot(dataframe, aes(x=question, y=freq, fill=answer)) +
    geom_bar(stat="identity", position="stack") +
    theme_minimal() +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + # Wrap labels to a width of 5 words
    coord_flip() +
    labs(title=graph_title,
         x="Question",
         y="Frequency (%)",
         fill="Answer") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
scale_fill_nejm()
}

## clean_matrix with variable
clean_matrix_eval <- function(dataframe, column_name, demographic_var) {
  cleaned_data <- dataframe %>%
    separate_rows({{ column_name }}, sep = "; ") %>%
    separate({{ column_name }}, into = c("question", "answer"), sep = " - ")
  cleaned_data$answer <- as.factor(cleaned_data$answer)
  
  summary_data <- cleaned_data %>%
    group_by( {{demographic_var}},question,answer) %>%
    summarise(n = n()) %>%
    mutate(freq = round((n / sum(n)),digits=2     )*100)
  
  return(summary_data)
}

## clean_matrix with variable
clean_matrix_eval_viz <- function(dataframe, demographic_var) {
   ggplot(dataframe, aes(x = !!sym(demographic_var), y = freq, fill = answer)) +
    geom_bar(stat = "identity", position = "fill") +  # Use 'fill' to stack the bars to 100%
    scale_y_continuous(labels = scales::percent_format()) +  # Use percent format for y-axis labels
    labs(y = "Percentage", x = "Vulnerability Level", fill = "Answer") +
    coord_flip() +  # Flip the axes to have vulnerability level on the y-axis
    theme_minimal() +
    theme(axis.text.x = element_text(hjust = 1)) +
 scale_fill_nejm()
}


### ### ### ### ### ### ### ### ### 
### Functions for BOX QUESTIONS ### 
### ### ### ### ### ### ### ### ### 

clean_box <- function(data, response) {
  summary_data <- data %>%
    group_by({{ response }}) %>%
    summarise(count = n()) %>%
    mutate(freq = round(count / sum(count), digits = 2)*100)
    names(summary_data)[1] <- "response"

  return(summary_data)
}

clean_box_eval <- function(data, column_name, demographic_var) {

# Calculate the total number of responses per vulnerable category
people <- air_survey_experiences %>%
  group_by({{demographic_var}}) %>%
  summarise(total = n())

# Calculate the summary data including frequencies
summary_data <- air_survey_experiences %>%
    group_by({{demographic_var}}, {{column_name}}) %>%
    summarise(n = n()) 

summary_data <- merge(summary_data,people, by = "vulnerable")

summary_data <- summary_data  %>%
  mutate(freq = round((n / total), digits = 2) * 100)
names(summary_data)[2] <- "question"
return(summary_data)
}

viz_clean_box_eval <- function(dataframe,graph_title) {
 
  # Create the bar chart
   # Create the bar chart with differentiation for 'vulnerable' levels within each 'question'
  ggplot(dataframe, aes(x=reorder(question, -freq), y=freq, fill=vulnerable)) +
    geom_bar(stat="identity", position="dodge") + # Use 'position=dodge' to place bars side by side
    theme_minimal() +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + # Wrap labels to a width of 40 characters
    coord_flip() +
    labs(title=graph_title,
         x="Response",
         y="Frequency (%)") +
    scale_fill_brewer(palette="Set1") + # Use a Brewer palette for distinguishable colors
    theme(axis.text.x = element_text(angle=45, hjust=1))
}



### ### ### ### ### ### ### ### ### #
### Functions for MULTI QUESTIONS ### 
### ### ### ### ### ### ### ### ### #

clean_multi <- function(data, response) {
  cleaned_data <- data %>%
    separate_rows({{ response }}, sep = "; ")
  
  summary_data <- cleaned_data %>%
    group_by({{ response }}) %>%
    summarise(count = n()) %>%
    mutate(freq = round(count / dim(data)[1], digits = 2) * 100)
      names(summary_data)[1] <- "response"

  return(summary_data)
}

clean_multi_eval <- function(data, column_name, demographic_var) {

# Calculate the total number of responses per vulnerable category
people <- data %>%
  group_by({{demographic_var}}) %>%
  summarise(total = n())


# Clean the data by separating rows and columns as required
cleaned_data <- data %>%
  separate_rows({{ column_name }}, sep = "; ") %>%
  separate({{ column_name }}, into = c("question"), sep = " - ")
print(cleaned_data)


# Calculate the summary data including frequencies
summary_data <- cleaned_data %>%
  #group_by({{demographic_var}}, question) %>%
  group_by(vulnerable, question) %>%
  summarise(n = n(), .groups = 'drop')

summary_data <- merge(summary_data,people, by = "vulnerable")

summary_data <- summary_data  %>%
  mutate(freq = round((n / total), digits = 2) * 100)

return(summary_data)
}

viz_clean_multi_eval <- function(dataframe,graph_title) {
 
  # Create the bar chart
   # Create the bar chart with differentiation for 'vulnerable' levels within each 'question'
  ggplot(dataframe, aes(x=reorder(question, -freq), y=freq, fill=vulnerable)) +
    geom_bar(stat="identity", position="dodge") + # Use 'position=dodge' to place bars side by side
    theme_minimal() +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + # Wrap labels to a width of 40 characters
    coord_flip() +
    labs(title=graph_title,
         x="Response",
         y="Frequency (%)") +
    scale_fill_brewer(palette="Set1") + # Use a Brewer palette for distinguishable colors
    theme(axis.text.x = element_text(angle=45, hjust=1))
}

####

viz_box_multi <- function(dataframe,graph_title) {
  # Order the dataframe by decreasing frequency
  ordered_df <- dataframe %>%
    arrange(desc(freq))
  
  # Create the bar chart
  ggplot(ordered_df, aes(x=reorder(response, -freq), y=freq)) +
    geom_bar(stat="identity", fill="blue") +
    theme_minimal() +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + # Wrap labels to a width of 5 words
    coord_flip() +
    labs(title=graph_title,
         x="Response",
         y="Frequency (%)") +
    theme(axis.text.x = element_text(angle=45, hjust=1))+
scale_fill_nejm()
}

### STATS ANALYSIS
clean_matrix_eval_chi <- function(questions_df) {
  results_list <- list() # Initialize an empty list to store the results dataframes
  
  # Loop through each unique question in the questions dataframe
  for(i in unique(questions_df$question)){
    data <- questions_df %>% filter(question == i)
    
    # Assuming 'vulnerable' is a column in your 'data' dataframe for categorization
    # You may need to adjust 'vulnerable' to the actual column name in 'summary_data'
    contingency_table <- xtabs(n ~ answer + vulnerable, data = data)
    chi_squared_test <- chisq.test(contingency_table,correct = TRUE)
    
    # Create a dataframe with the Chi-Squared test results
    results_df <- data.frame(
      question = i,
      statistic = chi_squared_test$statistic,
      pvalue = chi_squared_test$p.value,
      degreeof = chi_squared_test$parameter
    )
    
    # Store the results dataframe in the list
    results_list[[i]] <- results_df
  }
  
  # Combine all result dataframes in the list into a single dataframe
  final_results_df <- do.call(rbind, results_list)
  
  return(final_results_df)
}


clean_multi_eval_chi <- function(dataframe) {
  dataframe$total <- NULL
  dataframe$freq <- NULL
  dataframe$freq <- as.numeric(dataframe$n)
  dataframe$n <- NULL
 table_data <- xtabs(freq ~ vulnerable + question, data=dataframe)
 chi_square_result <- chisq.test(table_data)
 return(chi_square_result)
}

names(air_survey)[2:11] <- c('air_quality_experience',
 'pollution_health_impact',
 'pollution_sources_identification',
 'quality_change_perception',
 'vulnerable_populations_impact',
 'contaminants_awareness_knowledge',
 'sensor_location_suggestions',
 'improvement_actions_taken',
 'alert_reception_preference',
 'deployment_participation_interest')

## Questions to reconcile different text deployment_participation_interest, alert_reception_preference

```


# Air Quality Survey

1 **Do you feel you are experiencing air quality problems in your neighborhood? If so, what are the specific air quality problems, and how are they impacting you, your family, or your neighbors?**  (Open-ended)
  
2. **Have you or anyone you know experienced the following health issues related to poor air quality?** (Multi-choice)
  - Respiratory Issues  
  - Asthma  
  - Lung Cancer
  
3. **What do you think are the sources of air pollution in your community?** (Multi-choice)
  - Stationary sources (e.g., power plants, industrial facilities and factories, oil refineries)  
  - Mobile sources (e.g., cars, buses, trains)  
  - Natural sources (e.g., wind-blown dust)  
  - Pollution producing sites from agricultural areas, cities and wood-burning appliances  
 
4. **Have you noticed any changes in air quality in your community over the past 5 years?** (Select Box)
  - Yes, air quality has improved  
  - No, air quality has decreased  
  - I do not feel any changes in the air quality

5. **Do you feel that vulnerable populations (e.g., low-income individuals, children, elderly individuals) are disproportionately affected by air pollution in your community?** (Open-ended)
   

5. **Did you know Particulate matter (PM) and ground-level Ozone are common air contaminants harmful to human health?** (Multi-choice)
   - Yes  
   - No

6. **If you are providing suggestions for the city regarding where to install air quality monitoring sensors across Madison. Where would you like to see these sensors located?** (Multi-choice)
   - Shopping area  
   - Schools  
   - No, but I wish we did.  
   - No and I prefer not having them.

9. **Have you done anything to improve the air quality in your home or neighborhood? If so, what did you do? If not, what prevents you from taking action?** (Long text)


10. **If air quality becomes an issue and alerts need to be sent, how would you like to receive information about the air quality in your neighborhood?)**  (Multi-choice) 
    - Attending the community outreach event  
    - Connect with local working group to be the messenger to deliver this information to your neighborhood  


# Indices
These indices provide a composite score reflecting various factors, including economic, health, and environmental indicators, which can significantly affect community perceptions.

## [Social Vulnerability Index](https://www.atsdr.cdc.gov/placeandhealth/svi/index.html)
```{r}
#datatable(svi_response)
```

## [Environmental Justice Index Indicators](https://www.atsdr.cdc.gov/placeandhealth/eji/indicators.html)
```{r}
#datatable(eji_response)
```

## [Environmental Justice Index Indicators](https://www.epa.gov/ejscreen/ej-and-supplemental-indexes-ejscreen)
```{r}
#datatable(ejscreen_response)
```

# Analysis 

Comparative Analysis - Use comparative statistics (t-tests, ANOVA) to determine if there are statistically significant differences in responses between demographic groups, geographic locations, or SVI/EJI categories. For example, comparing the importance of tree benefits between communities with high vs. low vulnerability scores.

Regression Analysis - Conduct regression analyses (linear regression, logistic regression) to examine the relationship between demographic or SVI/EJI indicators and specific perceptions or attitudes. This can help identify factors that most strongly predict positive or negative perceptions. For example, if people from low vulnerability areas are more/less likely to report issues. 

Correlation Analysis - Explore correlations between SVI/EJI scores and survey responses to see if higher vulnerability or environmental injustice scores are associated with specific perceptions or concerns about trees and green spaces.


```{r, include=FALSE}

pol_impact <- clean_multi(air_survey,pollution_health_impact) # Multiple Response
pol_impact_viz <- viz_box_multi(pol_impact,"Health Issues")


pol_sources <- clean_multi(air_survey,pollution_sources_identification) #Multiple Response
pol_sources <- pol_sources[which(pol_sources$freq >0),]
pol_sources_viz <- viz_box_multi(pol_sources,"Pollution Sources Issues")

pol_changes <- clean_box(air_survey,quality_change_perception) # Single Response
pol_changes <- pol_changes[which(pol_changes$freq >0),]
pol_changes_viz <- viz_box_multi(pol_changes,"Community Air Quality Changes")

pol_contam <- clean_multi(air_survey,contaminants_awareness_knowledge)# Single Choice
pol_contam <- pol_contam[which(pol_contam$freq >0),]
pol_contam_viz <- viz_box_multi(pol_contam,"Awareness of Contaminants")

pol_sensor <- clean_multi(air_survey,sensor_location_suggestions) # Multiple Response 
pol_sensor <- pol_sensor[which(pol_sensor$freq >0),]
pol_sensor_viz <- viz_box_multi(pol_sensor,"Location of Sensors")

# Assuming your dataframe is named df and the column containing the text is named text_column
air_survey <- air_survey %>%
  mutate(alert_reception_preference = gsub("Newsletter from the city/county to your email", "Newsletters from the city/county to your email", alert_reception_preference),
         alert_reception_preference = gsub("neighborhood associations", "Neighborhood associations", alert_reception_preference))

pol_alerts <- clean_multi(air_survey,alert_reception_preference) # Multiple choice
pol_alerts <- pol_alerts[which(pol_alerts$freq >0),]
pol_alerts_viz <- viz_box_multi(pol_alerts,"Air Quality Alerts")


air_survey <- air_survey %>%
  mutate(deployment_participation_interest = gsub("Attending the community outreach event", "Attending a community outreach event", deployment_participation_interest),
         deployment_participation_interest = gsub("Connect with local working group to be the messenger to deliver this information to your neighborhood", "Connecting with local working group to be the messenger to deliver this information to your neighborhood", deployment_participation_interest))

pol_interest <- clean_box(air_survey,deployment_participation_interest) #  Single Response
pol_interest <- pol_interest[which(pol_interest$freq >0),]
pol_interest_viz <- viz_box_multi(pol_interest,"Deployment Interest")
```

# Air Quality Analysis

## Response Summary

### Health Issues Related to Trees
**Have you or anyone you know experienced the following health issues related to poor air quality?**

```{r}
datatable(pol_impact)
pol_impact_viz
```

### Community Pollution Sources

**What do you think are the sources of air pollution in your community**
```{r}
datatable(pol_sources)
pol_sources_viz
```

### Community Air Quality Changes 

**Have you noticed any changes in air quality in your community over the past 5 years?**
```{r}
datatable(pol_changes)
pol_changes_viz
```

### PM and Ground-level Ozone
**Did you know Particulate matter (PM) and ground-level Ozone are common air contaminants harmful to human health?**
```{r}
datatable(pol_contam)
pol_contam_viz
```

### Air Quality Monitors
**If you are providing suggestions for the city regarding where to install air quality monitoring sensors across Madison. Where would you like to see these sensors located?**
```{r}
datatable(pol_sensor)
pol_sensor_viz
```


### Being Informed about Air Quality
**If air quality becomes an issue and alerts need to be sent, how would you like to receive information about the air quality in your neighborhood?**
```{r}
datatable(pol_alerts)
pol_alerts_viz
```

### Deploying AQ Sensors Follow-up
**If there will be opportunities for you to participate in deciding where to deploy the air quality monitoring sensors. How would you like to be part of it? What roles would you like to take?**
```{r}
datatable(pol_interest)
pol_interest_viz
```


## Place Analysis for Air Quality
```{r place-analysis, include=FALSE, cache=FALSE}


air_survey <- merge(air_survey,participant_geographies,by="Member.ID",all.x = TRUE)

data_tracts_2010 <- as.character(c(unique(air_survey$Census_Tract_GEOID_2010)))
data_tracts_2020 <- as.character(c(unique(air_survey$Census_Tract_GEOID_2020)))


# https://www.atsdr.cdc.gov/placeandhealth/svi/index.html
svi_tract <- read.csv("/Volumes/cbjackson2/ccs-knowledge/census-data/svi/svi-wi-tract.csv")
svi_tract$FIPS <- as.character(svi_tract$FIPS)

svi_compute <- svi_tract[which(svi_tract$COUNTY %in% c("Dane")),]
Q1_svi <- quantile(svi_compute$RPL_THEMES, 0.25,na.rm = TRUE)
Q3_svi <- quantile(svi_compute$RPL_THEMES, 0.75,na.rm = TRUE)

svi_response <- svi_tract[which(svi_tract$FIPS %in% data_tracts_2020),]
not_svi_found <- data_tracts_2020[which(! data_tracts_2020 %in% svi_response$FIPS)] #6 of 82 not found in data
svi_response$vulnerable <- ifelse(svi_response$RPL_THEMES > Q3_svi, "High","Less severe")

#https://www.atsdr.cdc.gov/placeandhealth/eji/indicators.html
# Data Dictionary: Census tract boundaries are taken from 2019 TIGER/ Line Files and are based on the 2010 decennial census.   https://eji.cdc.gov/Documents/Data/2022/EJI_2022_Data_Dictionary_508.pdf

eji <- read.csv("//Volumes/cbjackson2/ccs-knowledge/census-data/environmental/eji-wisconsin.csv")
#eji <- eji[which(!is.na(eji$RPL_EBM)),]
eji_compute <- eji[which(eji$COUNTY %in% c("Dane")),]
# RPL_EBM is the rank environmental burden measure (EBM) while SPL_EBM is the composite score for the environmental burden measure
#Q1_eji <- quantile(eji_compute$RPL_EBM, 0.25,na.rm = TRUE) 
#Q3_eji <- quantile(eji_compute$RPL_EBM, 0.75,na.rm = TRUE)

Q1_eji <- quantile(eji_compute$SPL_EBM , 0.25,na.rm = TRUE) 
Q3_eji <- quantile(eji_compute$SPL_EBM , 0.75,na.rm = TRUE)

eji$geoid <- as.factor(eji$geoid)
eji_response <- eji[which(eji$geoid %in% data_tracts_2010),]
not_eji_found <- data_tracts_2010[which(! data_tracts_2010 %in% eji_response$geoid)] #17 of 82 not found in data
eji_response$vulnerable <- ifelse(eji_response$SPL_EBM > Q3_eji, "High","Less severe")

eji_response_analysis <- eji_response %>%
  dplyr::select(OBJECTID,statefp,countyfp,tractce,affgeoid,geoid,name,COUNTY,StateAbbr,StateDesc,Location,E_TOTPOP,SPL_EJI,RPL_EJI,RPL_EBM,SPL_EBM,EPL_OZONE,EPL_PM,EPL_DSLPM,EPL_TOTCR,SPL_EBM_THEME1,RPL_EBM_DOM1,vulnerable)
# Which indicators are important to include in the analysis? 



# Indicators: https://www.atsdr.cdc.gov/placeandhealth/eji/docs/EJI-2022-Indicators-508.pdf 
# Dictionary: https://eji.cdc.gov/Documents/Data/2022/EJI_2022_Data_Dictionary_508.pdf
# EJI -> Environmental Burden -> Air Pollution-> ALL (Ozone EPL_OZONE  ,PM2.5 EPL_PM  ,Disel Particulate Matter EPL_DSLPM, Air Toxic Cancer Risks EPL_TOTCR)
  # SPL_EBM_THEME1: Domain consisting of ozone, PM2.5, air toxics cancer risk, and diesel particulate matter. 
  # RPL_EBM_DOM1: Percentile rank of domain consisting of ozone, PM2.5, air toxics cancer risk, and diesel particulate matter.
# EJI -> Environmental Burden -> Built Environment -> (Recreational Parks)

# SPL_EJI: Summation of the HVM, EBI, and SVI module percentile ranks 
# RPL_EJI: Percentile ranks of SPL_EJI

eji_response_analysis$E_TOTPOP <- as.numeric(gsub(",", "", eji_response_analysis$E_TOTPOP))

#https://www.epa.gov/ejscreen/understanding-ejscreen-results
#ejscreen <- read.csv("/Volumes/cbjackson2/ccs-knowledge/census-data/environmental/ejm-wisconsin.csv")
#ejscreen_response <- ejscreen[which(ejscreen$Census.tract.2010.ID %in% data_tracts),]

# Which variables are important to include in the analysis?
```

# Categorizing Vulnerability 
```{r vulnerability, eval=TRUE, include=FALSE}
# Summarize our data
summary_eji <- eji_response_analysis %>%
  group_by(vulnerable) %>%
  summarise(across(.cols = 12:21, .fns = list(mean = ~mean(.x, na.rm = TRUE))))

summary_eji <- summary_eji %>% mutate_if(is.numeric, round, 3)

library(sf)          # for handling spatial data
library(tigris)
options(tigris_use_cache = TRUE)
options(scipen=999)


# Load the shapefile
#wisconsin_blocks <- st_read("/Volumes/cbjackson2/ccs-knowledge/ccs-data/geography/WI_CensusTL_BlockGroups_2020/WI_CensusTL_BlockGoups_2020.shp")
#wisconsin_tract <- st_read("/Volumes/cbjackson2/ccs-knowledge/ccs-data/geography/tl_2018_55_tract/tl_2018_55_tract.shp")
wisconsin_tract <- st_read("/Volumes/cbjackson2/ccs-knowledge/ccs-data/geography/tl_2019_55_tract//tl_2019_55_tract.shp")

# Filter to include only your tracts
#tree_survey$census_block_group <- substr(tree_survey$census_block_full, start = 1, stop = 12)
# Ensure the 'GEOID' format matches that of your dataframe and adjust "geoid" accordingly
target_tracts <- c(unique(air_survey$Census_Tract_GEOID_2010))
target_tracts <- as.character(target_tracts)
# Convert your 'geoid' values to character if they are not already, to ensure matching works
wisconsin_tracts_filtered <- wisconsin_tract %>%
    filter(as.character(GEOID) %in% target_tracts)

eji_response_analysis$geoid <- as.character(eji_response_analysis$geoid)


wisconsin_tracts_filtered <- left_join(wisconsin_tracts_filtered,eji_response_analysis[c("geoid","RPL_EJI","vulnerable")], by =c("GEOID"="geoid")) 

# Plot using ggplot2
county_data <- ggplot() +
  geom_sf(data = wisconsin_tracts_filtered, aes(fill = RPL_EJI), color = "black") +
    scale_fill_gradient(low = "lightblue", high = "darkblue", name = "RPL EJI Scale") + # Customize color scale as needed
  theme_minimal() +
   theme_bw() + theme(panel.border = element_blank(), 
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(), 
                      axis.line = element_blank(),
                      axis.text = element_blank(),
                      axis.ticks = element_blank()) +
  labs(title = "Environmental Burden Highlighted Census Tracts")

library(plotly)
```


```{r}
ggplotly(county_data)
```

In our analysis, we categorized vulnerability based on the Environmental Burden Module (RPL_EBM) percentile ranks derived from the 2022 Environmental Justice Index. To do this, we first determined the 25th (Q1) and 75th (Q3) percentile values of the RPL_EBM distribution. These percentile values served as thresholds to categorize regions based on their environmental burden. Specifically, regions with an RPL_EBM value greater than the 75th percentile (Q3) were categorized as "Most Vulnerable", indicating that they are in the top quartile of environmental burden and, therefore, face higher vulnerability to environmental injustices. Conversely, regions not exceeding this threshold were categorized as "Least Vulnerable". This method of categorization allows us to identify areas with the most significant environmental challenges and prioritize them for interventions and resource allocation.

```{r}
datatable(summary_eji)
```

```{r include=FALSE, warning=FALSE, }
air_survey$Census_Tract_GEOID_2010 <- as.character(air_survey$Census_Tract_GEOID_2010)
# Group people into least/most vulnerable areas 
air_survey <- left_join(air_survey, eji_response_analysis, by =c("Census_Tract_GEOID_2010"="geoid"))
air_survey_experiences <- air_survey
air_survey_experiences <- air_survey_experiences[which(!is.na(air_survey_experiences$vulnerable)),]


air_survey_experiences <- air_survey[which(!is.na(air_survey$vulnerable)),]
# Experiences with airquality


#prop_test_A <- prop.test(x = c(high_vuln_props["A"], low_vuln_props["A"]),
#                          n = c(sum(cont_table["High", ]), sum(cont_table["Low", ])),
#                          alternative = "two.sided")

vulnerable_q2 <- clean_multi_eval(air_survey_experiences,pollution_health_impact,vulnerable)
vulnerable_q2_viz <- viz_clean_multi_eval(vulnerable_q2,"Pollution Health Impacts")

names(vulnerable_q2)[3] <- "yes"
vulnerable_q2$no <- vulnerable_q2$total - vulnerable_q2$yes
vulnerable_q2 <- vulnerable_q2[which(!is.na(vulnerable_q2$question)),]
chi_squared_tests(vulnerable_q2)


vulnerable_q3 <- clean_multi_eval(air_survey_experiences,pollution_sources_identification,vulnerable)
vulnerable_q3_viz <- viz_clean_multi_eval(vulnerable_q3,"Pollution Sources Issues")

names(vulnerable_q3)[3] <- "yes"
vulnerable_q3$no <- vulnerable_q3$total - vulnerable_q3$yes
vulnerable_q3 <- vulnerable_q3[which(!is.na(vulnerable_q3$question)),]
chi_squared_tests(vulnerable_q3)

vulnerable_q4 <- clean_multi_eval(air_survey_experiences,quality_change_perception,vulnerable)
vulnerable_q4_viz <- viz_clean_multi_eval(vulnerable_q4,"Community Air Quality Changes")
names(vulnerable_q4)[3] <- "yes"
vulnerable_q4$no <- vulnerable_q4$total - vulnerable_q4$yes
vulnerable_q4 <- vulnerable_q4[which(!is.na(vulnerable_q4$question)),]
chi_squared_tests(vulnerable_q4)

vulnerable_q6 <- clean_multi_eval(air_survey_experiences,contaminants_awareness_knowledge,vulnerable)
vulnerable_q6_viz <- viz_clean_multi_eval(vulnerable_q6,"Awareness of Contaminants")
names(vulnerable_q6)[3] <- "yes"
vulnerable_q6$no <- vulnerable_q6$total - vulnerable_q6$yes
vulnerable_q6 <- vulnerable_q6[which(!is.na(vulnerable_q6$question)),]
chi_squared_tests(vulnerable_q6)

vulnerable_q7 <- clean_multi_eval(air_survey_experiences,sensor_location_suggestions,vulnerable)
vulnerable_q7_viz <- viz_clean_multi_eval(vulnerable_q7,"Location of Sensors")
names(vulnerable_q6)[3] <- "yes"
vulnerable_q7$no <- vulnerable_q7$total - vulnerable_q7$yes
vulnerable_q7 <- vulnerable_q7[which(!is.na(vulnerable_q7$question)),]
chi_squared_tests(vulnerable_q7)

vulnerable_q9 <- clean_multi_eval(air_survey_experiences,alert_reception_preference,vulnerable)
vulnerable_q9_viz <- viz_clean_multi_eval(vulnerable_q9,"Air Quality Alerts")
vulnerable_q9_chi <- clean_multi_eval_chi(vulnerable_q9)
vulnerable_q9_fisher <- clean_multi_eval_fisher(vulnerable_q9)

vulnerable_q10 <-clean_box_eval(air_survey_experiences,deployment_participation_interest,vulnerable)
vulnerable_q10_viz <- viz_clean_box_eval(vulnerable_q10,"Deployment Interest")
```

2. **Have you or anyone you know experienced the following health issues related to poor air quality?** (Multi-choice)  
- Respiratory Issues  
- Asthma  
- Lung Cancer

```{r}
datatable(vulnerable_q2)
vulnerable_q2_viz
vulnerable_q2_chi
```

3. **What do you think are the sources of air pollution in your community?** (Multi-choice)  
- Stationary sources (e.g., power plants, industrial facilities and factories, oil refineries)  
- Mobile sources (e.g., cars, buses, trains)   
- Natural sources (e.g., wind-blown dust)  
- Pollution producing sites from agricultural areas, cities and wood-burning appliances  

```{r}
datatable(vulnerable_q3)
vulnerable_q3_viz
vulnerable_q3_chi
```

4. **Have you noticed any changes in air quality in your community over the past 5 years?** (Select Box)  
- Yes, air quality has improved  
- No, air quality has decreased  
- I do not feel any changes in the air quality  

```{r}
datatable(vulnerable_q4)
vulnerable_q4_viz
datatable(vulnerable_q4_chi)
```

6. **Did you know Particulate matter (PM) and ground-level Ozone are common air contaminants harmful to human health?** (Multi-choice)  
- Yes   
- No  
```{r}
datatable(vulnerable_q6)
vulnerable_q6_viz
datatable(vulnerable_q6_chi)
```


7. **If you are providing suggestions for the city regarding where to install air quality monitoring sensors across Madison. Where would you like to see these sensors located?** (Multi-choice)  
- Shopping area  
- Schools  
- No, but I wish we did.  
- No and I prefer not having them.
```{r}
datatable(vulnerable_q7)
vulnerable_q7_viz
datatable(vulnerable_q7_chi)
```

9. **If air quality becomes an issue and alerts need to be sent, how would you like to receive information about the air quality in your neighborhood?** (Multi-choice) 

```{r}
datatable(vulnerable_q9)
vulnerable_q9_viz
datatable(vulnerable_q9_chi)
```

10. **If air quality becomes an issue and alerts need to be sent, how would you like to receive information about the air quality in your neighborhood?)**  (Multi-choice)   
- Attending the community outreach event  
- Connect with local working group to be the messenger to deliver this information to your neighborhood  

```{r}
datatable(vulnerable_q10)
vulnerable_q10_viz
#datatable(vulnerable_q10_chi)
```
