---
title: "CCS Knowledge Map Results: Tree Canopies"
author: "Corey Jackson"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true

---

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(DT)
library(ggsci)
library(gridExtra)
library(stringr)
library(broom) # For tidy chi-squared test results


# Import all datasets
tree_survey <- read.csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/tree-canopy/tree_survey.csv")
tree_map <- read.csv("/Volumes/cbjackson2/ccs-knowledge/ccs-data/tree-canopy/tree_map.csv")

tree_survey <- tree_survey %>%
  distinct(Contribution.ID, .keep_all = TRUE)

# Questions - https://docs.google.com/document/d/1hl5Eb66a8j7TDE1EzzOF4eUjUguet5dMsw7UJydr_uY/edit

### ### ### ### ### ### ### ### ### ## 
### Functions for MATRIX QUESTIONS ### 
### ### ### ### ### ### ### ### ### ##

clean_matrix <- function(dataframe, column_name) {
  cleaned_data <- dataframe %>%
    separate_rows({{ column_name }}, sep = "; ") %>%
    separate({{ column_name }}, into = c("question", "answer"), sep = " - ")
  cleaned_data$answer <- as.factor(cleaned_data$answer)
  
  summary_data <- cleaned_data %>%
    group_by(question, answer) %>%
    summarise(n = n()) %>%
    mutate(freq = round((n / sum(n)),digits=2     )*100)
  
  return(summary_data)
}

viz_matrix <- function(dataframe, graph_title) {
  ggplot(dataframe, aes(x=question, y=freq, fill=answer)) +
    geom_bar(stat="identity", position="stack") +
    theme_minimal() +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + # Wrap labels to a width of 5 words
    coord_flip() +
    labs(title=graph_title,
         x="Question",
         y="Frequency (%)",
         fill="Answer") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
scale_fill_nejm()
}

## clean_matrix with variable
clean_matrix_eval <- function(dataframe, column_name, demographic_var) {
  cleaned_data <- dataframe %>%
    separate_rows({{ column_name }}, sep = "; ") %>%
    separate({{ column_name }}, into = c("question", "answer"), sep = " - ")
  cleaned_data$answer <- as.factor(cleaned_data$answer)
  
  summary_data <- cleaned_data %>%
    group_by( {{demographic_var}},question,answer) %>%
    summarise(n = n()) %>%
    mutate(freq = round((n / sum(n)),digits=2     )*100)
  
  return(summary_data)
}

## clean_matrix with variable
clean_matrix_eval_viz <- function(dataframe, demographic_var) {
   ggplot(dataframe, aes(x = !!sym(demographic_var), y = freq, fill = answer)) +
    geom_bar(stat = "identity", position = "fill") +  # Use 'fill' to stack the bars to 100%
    scale_y_continuous(labels = scales::percent_format()) +  # Use percent format for y-axis labels
    labs(y = "Percentage", x = "Vulnerability Level", fill = "Answer") +
    coord_flip() +  # Flip the axes to have vulnerability level on the y-axis
    theme_minimal() +
    theme(axis.text.x = element_text(hjust = 1)) +
 scale_fill_nejm()
}


### ### ### ### ### ### ### ### ### 
### Functions for BOX QUESTIONS ### 
### ### ### ### ### ### ### ### ### 

clean_box <- function(data, response) {
  summary_data <- data %>%
    group_by({{ response }}) %>%
    summarise(count = n()) %>%
    mutate(freq = round(count / sum(count), digits = 2)*100)
    names(summary_data)[1] <- "response"

  return(summary_data)
}

clean_box_eval <- function(data, column_name, demographic_var) {

# Calculate the total number of responses per vulnerable category
people <- air_survey_experiences %>%
  group_by({{demographic_var}}) %>%
  summarise(total = n())

# Calculate the summary data including frequencies
summary_data <- air_survey_experiences %>%
    group_by({{demographic_var}}, {{column_name}}) %>%
    summarise(n = n()) 

summary_data <- merge(summary_data,people, by = "vulnerable")

summary_data <- summary_data  %>%
  mutate(freq = round((n / total), digits = 2) * 100)

return(summary_data)
}




### ### ### ### ### ### ### ### ### #
### Functions for MULTI QUESTIONS ### 
### ### ### ### ### ### ### ### ### #

clean_multi <- function(data, response) {
  cleaned_data <- data %>%
    separate_rows({{ response }}, sep = "; ")
  
  summary_data <- cleaned_data %>%
    group_by({{ response }}) %>%
    summarise(count = n()) %>%
    mutate(freq = round(count / dim(data)[1], digits = 2) * 100)
      names(summary_data)[1] <- "response"

  return(summary_data)
}

clean_multi_eval <- function(data, column_name, demographic_var) {

# Calculate the total number of responses per vulnerable category
people <- data %>%
  group_by({{demographic_var}}) %>%
  summarise(total = n())


# Clean the data by separating rows and columns as required
cleaned_data <- data %>%
  separate_rows({{ column_name }}, sep = "; ") %>%
  separate({{ column_name }}, into = c("question"), sep = " - ")
print(cleaned_data)


# Calculate the summary data including frequencies
summary_data <- cleaned_data %>%
  #group_by({{demographic_var}}, question) %>%
  group_by(vulnerable, question) %>%
  summarise(n = n(), .groups = 'drop')

summary_data <- merge(summary_data,people, by = "vulnerable")

summary_data <- summary_data  %>%
  mutate(freq = round((n / total), digits = 2) * 100)

return(summary_data)
}

viz_clean_multi_eval <- function(dataframe,graph_title) {
 
  # Create the bar chart
   # Create the bar chart with differentiation for 'vulnerable' levels within each 'question'
  ggplot(dataframe, aes(x=reorder(question, -freq), y=freq, fill=vulnerable)) +
    geom_bar(stat="identity", position="dodge") + # Use 'position=dodge' to place bars side by side
    theme_minimal() +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + # Wrap labels to a width of 40 characters
    coord_flip() +
    labs(title=graph_title,
         x="Response",
         y="Frequency (%)") +
    scale_fill_brewer(palette="Set1") + # Use a Brewer palette for distinguishable colors
    theme(axis.text.x = element_text(angle=45, hjust=1))
}

####

viz_box_multi <- function(dataframe,graph_title) {
  # Order the dataframe by decreasing frequency
  ordered_df <- dataframe %>%
    arrange(desc(freq))
  
  # Create the bar chart
  ggplot(ordered_df, aes(x=reorder(response, -freq), y=freq)) +
    geom_bar(stat="identity", fill="blue") +
    theme_minimal() +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) + # Wrap labels to a width of 5 words
    coord_flip() +
    labs(title=graph_title,
         x="Response",
         y="Frequency (%)") +
    theme(axis.text.x = element_text(angle=45, hjust=1))+
scale_fill_nejm()
}

### STATS ANALYSIS
clean_matrix_eval_chi <- function(questions_df) {
  results_list <- list() # Initialize an empty list to store the results dataframes
  
  # Loop through each unique question in the questions dataframe
  for(i in unique(questions_df$question)){
    data <- questions_df %>% filter(question == i)
    
    # Assuming 'vulnerable' is a column in your 'data' dataframe for categorization
    # You may need to adjust 'vulnerable' to the actual column name in 'summary_data'
    contingency_table <- xtabs(n ~ answer + vulnerable, data = data)
    chi_squared_test <- chisq.test(contingency_table)
    
    # Create a dataframe with the Chi-Squared test results
    results_df <- data.frame(
      question = i,
      statistic = chi_squared_test$statistic,
      pvalue = chi_squared_test$p.value,
      degreeof = chi_squared_test$parameter
    )
    
    # Store the results dataframe in the list
    results_list[[i]] <- results_df
  }
  
  # Combine all result dataframes in the list into a single dataframe
  final_results_df <- do.call(rbind, results_list)
  
  return(final_results_df)
}


clean_multi_eval_chi <- function(dataframe) {
  # Ensure 'n' is treated as numeric
  dataframe$n <- as.numeric(dataframe$n)
  
  results <- dataframe %>%
    group_by(question) %>%
    summarise(Least = sum(n[vulnerable == "Least"]),
              Most = sum(n[vulnerable == "Most"])) %>%
    rowwise() %>%
    do({
      chi_test_result <- chisq.test(c(.$Least, .$Most))
      data.frame(question = .$question,
                 statistic = round(chi_test_result$statistic, 3),
                 pvalue = round(chi_test_result$p.value, 3),
                 degreeof = round(as.numeric(chi_test_result$parameter), 3))
    }) %>%
    ungroup()
  
  return(results)
}

new_names <- c(
  "past_years","importance_of_benefits","agreement_about_trees","neighborhood_street_trees","tree_infrastructure_damage","tree_quality_life","tree_values","areas_needing_trees","preferred_tree_types","tree_goals","tree_support")

# Selecting the columns to rename by their position using the colnames function
colnames(tree_survey)[5:15] <- new_names
```

# Tree Canopy Survey

1a. **Over the past 10 years, the number of trees in my neighborhood has:**  
   - Increased  
   - Decreased  
   - Stayed the same  
   - Unsure

1b. **Over the past 10 years, the overall health and quality of trees (both public and private) in your neighborhood has:**  
   - Improved  
   - Declined  
   - Stayed the same

2. **How would you rate the overall care and maintenance of trees in your neighborhood?**  
   (Open-ended response)

3. **Please rate your level of agreement with each of the following statements:**  
   - Trees are important for maintaining a healthy community environment.  
   - Trees properly planted and cared for enhance the overall quality of life in a community.  
   - Trees properly planted and cared for improve the appearance of a community.

4. **Please rate the importance of each of the following benefits of trees:**  
   - Improve air quality by filtering airborne pollutants and dust.  
   - Improve water quality by controlling pollution, preventing erosion, and reducing flooding from stormwater runoff.  
   - Provide shading to maintain cooler temperatures.

5. **Which aspects of trees do you value? Select all that apply.**  
   - Shade, which cools neighborhoods and homes  
   - Cleaner air, by filtering air pollution  
   - The aesthetics or beauty that trees provide neighborhoods  
   - Mental health and emotional benefits  
   - The habitat and food source for wildlife that trees provide  
   - Environmental services that trees provide (carbon storage, storm water reduction, erosion control, etc.)  
   - The increase in property values  
   - Other (please specify)

6. **Does your neighborhood have planted street trees (Street trees- Any tree that is planted in the public right-of-way near and along the roadways which shade sidewalks and grow over the road)?**  
   - Yes, but I wish we didn't.  
   - Yes and I fully support having them.  
   - No, but I wish we did.  
   - No and I prefer not having them.

9. **Have you observed tree-related damage to infrastructure in your neighborhood? Select all that apply:**  
   - No, I have not observed tree-related damage to infrastructure  
   - Yes, damage to a street or sidewalk  
   - Yes, damage to overhead utilities (power lines, phone lines, etc.)  
   - Yes, damage to underground infrastructure (pipes, sewer lines, underground power lines, etc.)  
   - Other (please specify)

10. **Where would you like to see more trees planted? (Select up to three)**  
    - Street terrace  
    - Parks  
    - Apartment communities  
    - Commercial areas  
    - Parking lots  
    - Schools  
    - Along biking and walking paths  
    - Neighborhoods  
    - Other (please specify)

11. **What type of trees would you like to see planted?**  
    - Shade trees  
    - Fruit trees  
    - Evergreen trees  
    - No preference  
    - Other (please specify)

12. **If you are interested in helping to support the Town's tree planting efforts, which of the following activities would you be willing to participate in? Select all that apply.**  
    - None  
    - Volunteer or help organize a community tree planting event  
    - Attend an educational workshop (in person or virtual)  
    - Plant a tree on your private property  
    - Encourage your landlord to allow tree planting on a property you rent  
    - Volunteer to provide basic tree care in your neighborhood (watering and weeding)  
    - Other (please specify)

13. **If you are not interested or hesitant about planting a tree on your property, what are the contributing factor(s)? Select all that apply.**  
    - N/A  
    - Cost to maintain and trim trees  
    - Cost to water trees  
    - Mess caused by leaves, fruit, bark  
    - Damage to sewer pipes/sidewalks/driveways  
    - Risk of damage by falling branches  
    - Other (please specify)

14. **What tree related goals would you like to see prioritized? (Select up to three)**  
    - Increase the number of trees planted each year  
    - Maintain and preserve existing trees better  
    - Remove dead, dying, or otherwise hazardous trees  
    - Preserve trees better during development (keeping trees from getting removed as buildings and homes are built)  
    - Strengthen management strategies to reduce the risk of invasive pests and diseases  


# Indices
These indices provide a composite score reflecting various factors, including economic, health, and environmental indicators, which can significantly affect community perceptions.

## [Social Vulnerability Index](https://www.atsdr.cdc.gov/placeandhealth/svi/index.html)
```{r}
#datatable(svi_response)
```

## [Environmental Justice Index Indicators](https://www.atsdr.cdc.gov/placeandhealth/eji/indicators.html)
```{r}
#datatable(eji_response)
```

## [Environmental Justice Index Indicators](https://www.epa.gov/ejscreen/ej-and-supplemental-indexes-ejscreen)
```{r}
#datatable(ejscreen_response)
```

# Analysis 

Comparative Analysis - Use comparative statistics (t-tests, ANOVA) to determine if there are statistically significant differences in responses between demographic groups, geographic locations, or SVI/EJI categories. For example, comparing the importance of tree benefits between communities with high vs. low vulnerability scores.

Regression Analysis - Conduct regression analyses (linear regression, logistic regression) to examine the relationship between demographic or SVI/EJI indicators and specific perceptions or attitudes. This can help identify factors that most strongly predict positive or negative perceptions. For example, if people from low vulnerability areas are more/less likely to report issues. 

Correlation Analysis - Explore correlations between SVI/EJI scores and survey responses to see if higher vulnerability or environmental injustice scores are associated with specific perceptions or concerns about trees and green spaces.


```{r tc-setup, include=FALSE, cache=TRUE}
# Survey Population
demographics_hisp <- clean_box(tree_survey,hisp_code)
demographics_race <- clean_box(tree_survey,race_recode)
demographics_income <-clean_box(tree_survey,income_recode)
demographics_education <- clean_box(tree_survey,edu_recode)
demographics_tract <- clean_box(tree_survey,census_tract_full)
demographics_county <- clean_box(tree_survey,county_fips)

demo_vars <- c("edu_recode","hisp_code","race_recode","income_recode","Gender")

# QUESTION SUMMARY
trees_overtime <- clean_matrix(tree_survey,"past_years")
trees_overtime_viz <- viz_matrix(trees_overtime,"Beliefs about Trees")
trees_overtime_eval <-  clean_matrix_eval(tree_survey,"past_years",edu_recode)


eval_summary <- function(tree_survey, past_years, demographic_variable) {
  # Your existing implementation of the function
}

# List of demographic variables
demo_vars <- c("edu_recode","hisp_code","race_recode","income_recode","Gender")

# Function to loop through demo_vars and apply clean_matrix_eval
process_and_save_results <- function(tree_survey, past_years) {
  results_list <- list() # Create an empty list to store results
  
  for(demo_var in demo_vars) {
    # Apply the clean_matrix_eval function for each demographic variable
    result <- clean_matrix_eval(tree_survey, "past_years", "demo_var")
  
    # Extract the first word of the demographic variable for naming
    var_name_first_word <- strsplit(demo_var, "_")[[1]][1]
    
    # Construct the new dataframe name
    dataframe_name <- paste("trees_overtime", var_name_first_word, sep = "_")
    
    # Save the result with the constructed name
    results_list[[dataframe_name]] <- result
  }
  
  # Optionally, return all results as a list if you need to use them later in the same session
  return(results_list)
}

# You would call this function with your tree_survey dataframe and past_years column as follows:
 results <- process_and_save_results(tree_survey, past_years)

# Note: This script assumes that your clean_matrix_eval function returns a dataframe
# and that you have a predefined tree_survey dataframe and past_years column to work with.


#trees_overtime_eval_viz <- clean_matrix_eval_viz(trees_overtime_eval,"edu_recode")

###
tree_benefits <- clean_matrix(tree_survey,"importance_of_benefits")
tree_benefits_viz <- viz_matrix(tree_benefits,"Benefits of Trees")

###
tree_beliefs <- clean_matrix(tree_survey,"agreement_about_trees")
tree_beliefs_edu <- clean_matrix_eval(tree_survey,"agreement_about_trees",edu_recode)
tree_beliefs_viz <- viz_matrix(tree_beliefs,"Beliefs about Trees")

###
trees_home <- clean_box(tree_survey,neighborhood_street_trees)
trees_home_viz <- viz_box_multi(trees_home,"Trree")
###
tree_damage <- clean_multi(tree_survey,tree_infrastructure_damage)
tree_damage_viz <- viz_box_multi(tree_damage,"Trree")

###
tree_value <- clean_multi(tree_survey,tree_values)
tree_value <- tree_value[which(tree_value$freq>0),]
tree_value_viz <- viz_box_multi(tree_value,"Trree")

###
tree_area_need <- clean_multi(tree_survey,areas_needing_trees)
tree_area_need_viz <- viz_box_multi(tree_area_need,"Trree")

###
tree_types <- clean_multi(tree_survey,preferred_tree_types)
tree_types <- tree_types[which(tree_types$freq>0),]
tree_types_viz <- viz_box_multi(tree_types,"Trree")

###
tree_goals <- clean_multi(tree_survey,tree_goals)
tree_goals_viz <- viz_box_multi(tree_goals,"Trree")

###
tree_support <- clean_multi(tree_survey,tree_support)
tree_support_viz <- viz_box_multi(tree_support,"Trree")

```


# Tree Canopy Analysis

## Survey Population
```{r}
datatable(demographics_hisp)
```

```{r}
datatable(demographics_race)
```

```{r}
datatable(demographics_income)
```

```{r}
datatable(demographics_education)
```

```{r}
datatable(demographics_tract)
```

```{r}
datatable(demographics_county)
```

## Response Summary

###  Tree Change

**Over the past 10 years, the number of trees in my neighborhood has:**  
   - Increased  
   - Decreased  
   - Stayed the same  
   - Unsure

**Over the past 10 years, the overall health and quality of trees (both public and private) in your neighborhood has:**  
   - Increased  
   - Decreased  
   - Stayed the same  
   - Unsure

```{r tc-analysis-report, echo=TRUE}
datatable(trees_overtime)
trees_overtime_viz
```

### Agreement on Tree Benefits

**Please rate the importance of each of the following benefits of trees:**  
   - Improve air quality by filtering airborne pollutants and dust.  
   - Improve water quality by controlling pollution, preventing erosion, and reducing flooding from stormwater runoff.  
   - Provide shading to maintain cooler temperatures.

```{r}
datatable(tree_benefits)
tree_benefits_viz
```

### Importance of Tree Benefits

**Please rate your level of agreement with each of the following statements:**  
   - Trees are important for maintaining a healthy community environment.  
   - Trees properly planted and cared for enhance the overall quality of life in a community.  
   - Trees properly planted and cared for improve the appearance of a community.
   
```{r}
datatable(tree_beliefs)
tree_beliefs_viz
```

### Neighborhood Street Trees Presence

**Does your neighborhood have planted street trees (Street trees- Any tree that is planted in the public right-of-way near and along the roadways which shade sidewalks and grow over the road)?**  
   - Yes, but I wish we didn't.  
   - Yes and I fully support having them.  
   - No, but I wish we did.  
   - No and I prefer not having them.
```{r}
datatable(trees_home)
trees_home_viz
```

### Tree-Related Infrastructure Damage

**Have you observed tree-related damage to infrastructure in your neighborhood? Select all that apply:**  
   - No, I have not observed tree-related damage to infrastructure  
   - Yes, damage to a street or sidewalk  
   - Yes, damage to overhead utilities (power lines, phone lines, etc.)  
   - Yes, damage to underground infrastructure (pipes, sewer lines, underground power lines, etc.)  
   - Other (please specify)
```{r}
datatable(tree_damage)
tree_damage_viz
```

### Trees and Quality of Life
```{r}
# OPEN ENDED NEED TO PROCESS USING TEXT MINING
```

### Valued Tree Aspects

**Which aspects of trees do you value? Select all that apply.**  
   - Shade, which cools neighborhoods and homes  
   - Cleaner air, by filtering air pollution  
   - The aesthetics or beauty that trees provide neighborhoods  
   - Mental health and emotional benefits  
   - The habitat and food source for wildlife that trees provide  
   - Environmental services that trees provide (carbon storage, storm water reduction, erosion control, etc.)  
   - The increase in property values  
   - Other (please specify)
```{r}
datatable(tree_value)
tree_value_viz
```

### Preferred Tree Planting Locations

**Where would you like to see more trees planted? (Select up to three)**  
    - Street terrace  
    - Parks  
    - Apartment communities  
    - Commercial areas  
    - Parking lots  
    - Schools  
    - Along biking and walking paths  
    - Neighborhoods  
    - Other (please specify)
```{r}
datatable(tree_area_need)
tree_area_need_viz
```

### Desired Types of Trees
```{r}
datatable(tree_types)
tree_types_viz
```

### Tree-Related Priority Goals

**What tree related goals would you like to see prioritized? (Select up to three)**  
    - Increase the number of trees planted each year  
    - Maintain and preserve existing trees better  
    - Remove dead, dying, or otherwise hazardous trees  
    - Preserve trees better during development (keeping trees from getting removed as buildings and homes are built)  
    - Strengthen management strategies to reduce the risk of invasive pests and diseases  
```{r}
datatable(tree_goals)
tree_goals_viz
```

### Support for Tree Planting

**If you are interested in helping to support the Town's tree planting efforts, which of the following activities would you be willing to participate in? Select all that apply.**  
    - None  
    - Volunteer or help organize a community tree planting event  
    - Attend an educational workshop (in person or virtual)  
    - Plant a tree on your private property  
    - Encourage your landlord to allow tree planting on a property you rent  
    - Volunteer to provide basic tree care in your neighborhood (watering and weeding)  
    - Other (please specify)
```{r}
datatable(tree_support)
tree_support_viz
```


## Place Analysis for Tree Canopies
```{r place-analysis, include=FALSE, cache=FALSE}

# The EJ dataframe has descriptions of their neighborhoods, we could examine perceptions and solutions. We might need to highlight contrasting (interesting) insights. Depending on match, we could make argument for more knowledge about harms

# tree_survey <- tree_survey %>%
#   mutate(
#     county_code = sprintf("%03d", as.integer(county_fips)),
#     census_tract = sprintf("%06d", as.integer(census_tract)),
#     census_block = sprintf("%04d", as.integer(census_block)),
#     census_tract_full = paste0(state_fips, county_code, census_tract),
#     census_block_full = paste0(state_fips, county_code, census_tract, census_block),
#   )

data_tracts <- c(unique(tree_survey$census_tract_full))
data_blocks <- c(unique(tree_survey$census_block_full))

# https://www.atsdr.cdc.gov/placeandhealth/svi/index.html
#svi_tract <- read.csv("/Volumes/cbjackson2/ccs-knowledge/census-data/svi/svi-wi-tract.csv")
#svi_response <- svi_tract[which(svi_tract$FIPS %in% data_tracts),]

# Which variables are important to include in the analysis?

#https://www.atsdr.cdc.gov/placeandhealth/eji/indicators.html
eji <- read.csv("//Volumes/cbjackson2/ccs-knowledge/census-data/environmental/eji-wisconsin.csv")
eji <- eji[which(!is.na(eji$RPL_EBM)),]
eji <- eji[which(eji$COUNTY %in% c("Dane","Jefferson")),]

# Calculate quartiles
Q1 <- quantile(eji$RPL_EBM, 0.25)
Q3 <- quantile(eji$RPL_EBM, 0.75)

eji_response <- eji[which(eji$geoid %in% data_tracts),]
eji_response$vulnerable <- ifelse(eji_response$RPL_EBM > Q3, "Least","Most")
eji_response_analysis <- eji_response %>%
  dplyr::select(OBJECTID,statefp,countyfp,tractce,affgeoid,geoid,name,COUNTY,StateAbbr,StateDesc,Location,E_TOTPOP,SPL_EJI,RPL_EJI,RPL_EBM,EPL_OZONE,EPL_PM,EPL_DSLPM,EPL_TOTCR,SPL_EBM_THEME1,RPL_EBM_DOM1,vulnerable)
# Which indicators are important to include in the analysis? 

# Indicators: https://www.atsdr.cdc.gov/placeandhealth/eji/docs/EJI-2022-Indicators-508.pdf 
# Dictionary: https://eji.cdc.gov/Documents/Data/2022/EJI_2022_Data_Dictionary_508.pdf
# EJI -> Environmental Burden -> Air Pollution-> ALL (Ozone EPL_OZONE  ,PM2.5 EPL_PM  ,Disel Particulate Matter EPL_DSLPM, Air Toxic Cancer Risks EPL_TOTCR)
#   SPL_EBM_THEME1: Domain consisting of ozone, PM2.5, air toxics cancer risk, and diesel particulate matter. 
#   RPL_EBM_DOM1: Percentile rank of domain consisting of ozone, PM2.5, air toxics cancer risk, and diesel particulate matter.
# EJI -> Environmental Burden -> Built Environment -> (Recreational Parks)

# SPL_EJI: Summation of the HVM, EBI, and SVI module percentile ranks 
# RPL_EJI: Percentile ranks of SPL_EJI

eji_response_analysis$E_TOTPOP <- as.numeric(gsub(",", "", eji_response_analysis$E_TOTPOP))


#https://www.epa.gov/ejscreen/understanding-ejscreen-results
#ejscreen <- read.csv("/Volumes/cbjackson2/ccs-knowledge/census-data/environmental/ejm-wisconsin.csv")
#ejscreen_response <- ejscreen[which(ejscreen$Census.tract.2010.ID %in% data_tracts),]

# Which variables are important to include in the analysis?


#The first 2 digits represent the state FIPS (Federal Information Processing Standards) code.
#The next 3 digits are for the county within that state.
#Following 6 digits are for the census tract within the county.
#The next 1 to 4 digits (of which you're interested in the first part) represent the block group or block, which are subdivisions of census tracts.
######### Decide which tracts are vulnerable. Make respondents in two groups.
```

### Categorizing Vulnerability 
```{r vulnerability, eval=TRUE, include=FALSE}
# Summarize our data

summary_eji <- eji_response_analysis %>%
  group_by(vulnerable) %>%
  summarise(across(.cols = 12:21, .fns = list(mean = ~mean(.x, na.rm = TRUE))))

summary_eji <- summary_eji %>% mutate_if(is.numeric, round, 3)


library(sf)          # for handling spatial data
library(tigris)
options(tigris_use_cache = TRUE)
options(scipen=999)


# Load the shapefile
#wisconsin_blocks <- st_read("/Volumes/cbjackson2/ccs-knowledge/ccs-data/geography/WI_CensusTL_BlockGroups_2020/WI_CensusTL_BlockGoups_2020.shp")

wisconsin_tract <- st_read("/Volumes/cbjackson2/ccs-knowledge/ccs-data/geography/tl_2018_55_tract/tl_2018_55_tract.shp")

# Filter to include only your tracts
#tree_survey$census_block_group <- substr(tree_survey$census_block_full, start = 1, stop = 12)
# Ensure the 'GEOID' format matches that of your dataframe and adjust "geoid" accordingly
target_tracts <- c(unique(tree_survey$census_tract_full))

# Convert your 'geoid' values to character if they are not already, to ensure matching works
wisconsin_tracts_filtered <- wisconsin_tract %>%
    filter(as.character(GEOID) %in% target_tracts)

eji_response_analysis$geoid <- as.character(eji_response_analysis$geoid)

wisconsin_tracts_filtered <- left_join(wisconsin_tracts_filtered,eji_response_analysis[c("geoid","RPL_EJI","vulnerable")], by =c("GEOID"="geoid"))

# Plot using ggplot2
county_data <- ggplot() +
  geom_sf(data = wisconsin_tracts_filtered, aes(fill = RPL_EJI), color = "black") +
    scale_fill_gradient(low = "lightblue", high = "darkblue", name = "EJI ranking") + # Customize color scale as needed
  theme_minimal() +
   theme_bw() + theme(panel.border = element_blank(), 
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(), 
                      axis.line = element_blank(),
                      axis.text = element_blank(),
                      axis.ticks = element_blank()) +
  labs(title = "Environmental Burden Highlighted Census Tracts")
```

```{r}
county_data
```


In our analysis, we categorized vulnerability based on the Environmental Burden Module (RPL_EBM) percentile ranks derived from the 2022 Environmental Justice Index. To do this, we first determined the 25th (Q1) and 75th (Q3) percentile values of the RPL_EBM distribution. These percentile values served as thresholds to categorize regions based on their environmental burden. Specifically, regions with an RPL_EBM value greater than the 75th percentile (Q3) were categorized as "Most Vulnerable", indicating that they are in the top quartile of environmental burden and, therefore, face higher vulnerability to environmental injustices. Conversely, regions not exceeding this threshold were categorized as "Least Vulnerable". This method of categorization allows us to identify areas with the most significant environmental challenges and prioritize them for interventions and resource allocation.

```{r}
datatable(summary_eji)
```

```{r include=FALSE, warning=FALSE}
tree_survey$census_tract_full <- as.character(tree_survey$census_tract_full)
# Group people into least/most vulnerable areas 
tree_survey <- left_join(tree_survey, eji_response_analysis, by =c("census_tract_full"="geoid"))
#tree_survey

# Experiences with tree canopies
tree_survey_experiences <- tree_survey[c(3,5,9,11,12,14,15,86)]

tree_survey_experiences <- tree_survey_experiences[which(!is.na(tree_survey_experiences$vulnerable)),]
vulnerable_q5 <- clean_matrix_eval(tree_survey_experiences,"past_years",vulnerable)
vulnerable_q5$answer <- factor(vulnerable_q5$answer, levels = rev(c("Decreased", "Stayed the same", "Increased", "I do not know")))

vulnerable_q5_a <- vulnerable_q5[which(vulnerable_q5$question==unique(vulnerable_q5$question)[1]),]
vulnerable_q5_b <- vulnerable_q5[which(vulnerable_q5$question==unique(vulnerable_q5$question)[2]),]
vulnerable_q5viz_a <- clean_matrix_eval_viz(vulnerable_q5_a,"vulnerable")
vulnerable_q5viz_b <-  clean_matrix_eval_viz(vulnerable_q5_b,"vulnerable")

# print(results)
```


2. **Over the past 10 years, the number of trees in my neighborhood has:**  
   - Increased  
   - Decreased  
   - Stayed the same  
   - Unsure
   
```{r}
datatable(vulnerable_q5_a) 
vulnerable_q5viz_a
#datatable(vulnerable_q5_chi_a)
```
   

3. **Over the past 10 years, the overall health and quality of trees (both public and private) in your neighborhood has:**  
   - Improved  
   - Declined  
   - Stayed the same

```{r}
datatable(vulnerable_q5_b) 
vulnerable_q5viz_b
#datatable(vulnerable_q5_chi_b)
```


```{r include = FALSE, warning=FALSE}
vulnerable_q9 <- clean_multi_eval(tree_survey_experiences,tree_infrastructure_damage,vulnerable)
vulnerable_q9_viz <- viz_clean_multi_eval(vulnerable_q9,"Tree Related Damage in My Community")
vulnerable_q9_chi <- clean_multi_eval_chi(vulnerable_q9)
```

```{r}
datatable(vulnerable_q9)
vulnerable_q9_viz
datatable(vulnerable_q9_chi)
```

```{r, include = FALSE, warning=FALSE}
vulnerable_q11 <- clean_multi_eval(tree_survey_experiences,tree_values,vulnerable)
vulnerable_q11_viz <- viz_clean_multi_eval(vulnerable_q11,"Tree Values")
vulnerable_q11_chi <- clean_multi_eval_chi(vulnerable_q11)
```

```{r}
datatable(vulnerable_q11)
vulnerable_q11_viz
datatable(vulnerable_q11_chi)
```
```{r, include=FALSE, echo=FALSE, warning=FALSE}
vulnerable_q12 <- clean_multi_eval(tree_survey_experiences,areas_needing_trees,vulnerable)
vulnerable_q12_viz <- viz_clean_multi_eval(vulnerable_q12,"Tree Needs")
vulnerable_q12_chi <- clean_multi_eval_chi(vulnerable_q12)
```

```{r}
datatable(vulnerable_q12)
vulnerable_q12_viz
datatable(vulnerable_q12_chi)
```
```{r, include=FALSE}
vulnerable_q14 <- clean_multi_eval(tree_survey_experiences,tree_goals,vulnerable)
vulnerable_q14_viz <- viz_clean_multi_eval(vulnerable_q14,"Tree Goals")
vulnerable_q14_chi <- clean_multi_eval_chi(vulnerable_q14)
```

```{r}
datatable(vulnerable_q14)
vulnerable_q14_viz
datatable(vulnerable_q14_chi)
```

```{r, include=FALSE}
vulnerable_q15 <- clean_multi_eval(tree_survey_experiences,tree_support,vulnerable)
vulnerable_q15_viz <- viz_clean_multi_eval(vulnerable_q15,"Tree Support")
vulnerable_q15_chi <- clean_multi_eval_chi(vulnerable_q15)
```

```{r}
datatable(vulnerable_q15)
vulnerable_q15_viz
datatable(vulnerable_q15_chi)
```


