---
title: "CCS Knowledge Map Results"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true

---

```{r setup, include=FALSE}
# Import all datasets


# Clean and transform data when necessary

```

# Project Overview

# Local Government Survey Descriptions

## Air Quality (AQ)

```{r aq-setup, include=FALSE, cache=TRUE}

# Run all analysis for the AQ survey here

```

- Description of survey and the questions asked


### AQ Analysis
```{r aq-analysis-report, echo=TRUE}

# Report the analysis of survey items here

```

### AQ Map
```{r aq-map-report, echo=TRUE}

# Report the analysis of map items here

```


## Urban Heat (UH)
```{r uh-setup, include=FALSE, cache=TRUE}

# Run all analysis for the AQ survey here

```

- Description of survey and the questions asked

### UH Analysis
```{r uh-analysis-report, echo=TRUE}

# Report the analysis of survey items here

```

### UH Map
```{r uh-map-report, echo=TRUE}

# Report the analysis of survey items here

```

## Tree Canopies (TC)
```{r tc-setup, include=FALSE, cache=TRUE}

# Run all analysis for the AQ survey here

```

- Description of survey and the questions asked


### TC Analysis
```{r tc-analysis-report, echo=TRUE}

# Report the analysis of survey items here

```


### TC Map
```{r tc-map-report, echo=TRUE}

# Report the analysis of survey items here

```


# Environmental Justics Survey Descriptions

## EJ Stories 
```{r ej-stories-setup, include=FALSE, cache=TRUE}

```

- Description of survey and the questions asked


## EJ Solutions
```{r ej-solutions-setup, include=FALSE, cache=TRUE}

```

- Description of survey and the questions asked


# Meta Summary

